---
title: "Untitled"
format: html
---

```{r setup}

knitr::opts_chunk$set(echo = FALSE, fig.width=9, message = FALSE, warning=FALSE)

library(tidyverse)
library(sf)
library(readxl)
library(kableExtra)
library(flextable)
library(viridis)
library(scales)
library(janitor)
library(cowplot)
library(magick)
library(patchwork)
library(shadowtext)
library(showtext)
library(ggrepel)
library(terra)
library(tidyterra)
library(maptiles)
library(cowplot)
library(ggview)

# showtext_auto()

# font_add_google("Roboto", "roboto")

`%out%` <- Negate(`%in%`)

theme_set(theme_light())

options(scipen = 999)

range_wna <- function(x){(x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))}

```

# Data

## Geodata

```{r}

nepal_admin <- read_xlsx("./data/npl_admin_boundaries.xlsx", 
                         sheet = 7) |> 
  select(adm3_name, adm3_pcode, adm2_name, adm2_pcode, adm1_name, adm1_pcode)

affected_municipalities_wards <- read_xls("./data/Affected_wardsv2.xls") |> 
  janitor::clean_names() |> 
  select(adm1_pcode, 
         district = adm2_en, 
         adm2_pcode,
         municipality = adm3_en, 
         adm3_pcode, 
         ward = new_ward_n) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = "adm1_pcode"
  ) |> 
  rename(province = adm1_name) |> 
  relocate(province, .before = adm1_pcode) |> 
  distinct(adm3_pcode, ward)

wards <- st_read("./data/shapefiles/npl_admn_ad4_py_s1_ocha_hp_wards.shp") |> 
  rename(ward = NEW_WARD_N) |> 
  janitor::clean_names() |> 
  mutate(district = str_to_title(district)) |> 
  rename(affected_old = affected)

affected_wards <- read_xls("./data/Affected_wardsV2.xls") |> 
  janitor::clean_names()

adm3 <- st_read("./data/shapefiles/npl_admin_boundaries.shp/npl_admin3.shp")

adm2 <- st_read("./data/shapefiles/npl_admin_boundaries.shp/npl_admin2.shp")

river_buffer <- st_read("./data/shapefiles/aoi_affd_aff_py_s3_govn_pp_AOI500mBuffer.shp") 

river <- st_read("./data/shapefiles/Flood Extent Shape file/Flood extent_SHP.shp")

holding_centres <- st_read("./data/shapefiles/npl_shel_shl_pt_s3_various_pp_holding_centre.shp") 

# river <- st_read("./data/shapefiles/Flood Extent.gpkg", options = "CONVERT_TO_LINEAR=YES") 

```



## Damage and response data

```{r}

municipal_damage_losses <- read_csv("./data/municipal_damage_loss.csv")

municipal_long <- municipal_damage_losses |> 
  mutate(affected_hectares_agriculture = paddy_affected_hectares + vegetables_affected_hectares, 
         total_baseline_hectares = paddy_baseline_hectares + vegetables_baseline_hectares, 
         pc_affected_hectares = affected_hectares_agriculture / total_baseline_hectares, 
         pc_affected_buildings = affected_buildings / estimated_buildings_in_damaged_corridor, 
         pc_impacted_households = impacted_households / households_in_affected_wards_census_2021) |> 
  select(adm2_pcode, adm3_pcode, impacted_households, 
         pc_impacted_households, 
         impacted_population = impacted_population_total,
         affected_buildings, pc_affected_buildings,
         affected_hectares_agriculture, pc_affected_hectares) |> 
  pivot_longer(cols = impacted_households:pc_affected_hectares, 
               names_to = "variable", 
               values_to = "value") 

consolidated <- read_xlsx("./data/NEPAL 5W Data Consolidation (ADMIN_ONLY)_23 Sep 2026.xlsx", 
                          skip = 5, 
                          sheet = "Compiled_Data") |> 
  clean_names() |> 
  filter(disaster_response_plan %in% c("Rasuwa Flood Response", "Rasuwa Flood Respnese")) |> 
  mutate_at(c("province", "district", "municipality"), ~ str_to_title(.)) |> 
  mutate_at(c("province", "district", "municipality"), ~ str_trim(.)) |> 
  mutate(municipality = str_remove_all(municipality, " Gaunpalika"), 
         municipality = str_remove_all(municipality, " Rural Municipality"), 
         municipality = str_remove_all(municipality, " Municipality")) |>
  mutate(municipality = case_when(
    municipality == "Benighat" ~ "Benighat Rorang", 
    municipality == "Galchi Rural Municipality" ~ "Galchhi", 
    municipality == "Gandaki" ~ "Gandaki", 
    municipality == "Bheri Malika Municipality" ~ "Bheri Malika", 
    municipality == "Nalgad Municipality" ~ "Nalgad", 
    municipality == "Kathmandu Metropolitian City" ~ "Kathmandu", 
    municipality == "Nagarjun Municipality" ~ "Nagarjun", 
    municipality == "Belkotgadhi Municipality|Belkotgadhi Nagarpalika" ~ "Belkotgadhi", 
    str_detect(municipality, "Langtang") ~ "Langtang", 
    str_detect(municipality, "Bidur") ~ "Bidur", 
    municipality == "Kispang Municipality" ~ "Kispang", 
    municipality == "Tarkeshwor" ~ "Tarakeshwor", 
    municipality == "Rasuwa Dao, Dhunche" ~ "Gosaikunda",
    str_detect(municipality, "Devghat") ~ "Devghat", 
    str_detect(municipality, "Gandaki") ~ "Gandaki", 
    str_detect(municipality, "Belkotgadhi") ~ "Belkotgadhi", 
    str_detect(municipality, "Langtang") ~ "Langtang",
    municipality == "Aanbukhaireni" ~ "Aanbu Khaireni",
    TRUE ~ municipality)) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm3_pcode != "NP0328596") |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  ) |> 
  rename(individuals_reached = total_number_of_beneficiaries_reached_people_individuals) |> 
  filter(disaster_response_plan == "Rasuwa Flood Response")

# census_individual <- read_csv("./data/nepal_census2021_ward_level_individual_tables_bagmati_gandaki_long.csv")

# Using this temporarily until the population figures are resolved
differences <- read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv")

damage_points <- read_xlsx("./data/Consolidated Damage.xlsx") |> 
  clean_names() |> 
  rename(x = long, y = lat)

differences <- read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv")

census_flat <- cbind(
  read_csv("./data/nepal_census2021_ward_level_household_tables_bagmati_gandaki_flat.csv") |> 
    mutate(match1 = paste0(adm2_pcode, adm3_pcode, ward)),
  read_csv("./data/nepal_census2021_ward_level_individual_tables_bagmati_gandaki_flat.csv") |> 
    mutate(match2 = paste0(adm2_pcode, adm3_pcode, ward)) |> 
    select(-c(province:ward), -total_households, -rdna_affected)
)

affected_municipalities_17 <- read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx") |> 
  clean_names()

register <- read_xlsx("./data/Nepal - Assessment registry - Rasuwa Flood.xlsx", skip = 3) |> 
  setNames(c("lead_organisation", "participating_organisation", 
             "assessment", "description", "sector", 
             "province", "district", "municipality", "ward", 
             "representative_at_level", "status", "status_update", 
             "data_collection_method", "availability_report", "email_contact", 
             "permission_public", "report_link", "dashboard_link", 
             "comments"))

impacted_buildings <- read_xlsx("./data/impacted_buildings.xlsx") |> 
  mutate(municipality = ifelse(municipality == "Ichcha Kamana", 
                               "Ichchha Kamana", 
                               municipality)) |> 
  left_join(
    nepal_admin |> 
      distinct(adm3_name, adm1_pcode, adm2_pcode, adm3_pcode), 
    by = c("municipality" = "adm3_name")
  ) |> 
  filter(adm3_pcode != "NP0327301" & adm3_pcode != "NP0335301")

proj_flat <- read_csv("./data/population_projections_2026_affected_wards_flat.csv")

# Logos
combined_logos <- grid::rasterGrob(image_append(
  c(image_read("./plots/logos/UN Nepal-Logo_horizontal_match_size.png"),
    image_read("./plots/logos/002_COMM_GUID_iMMAPLogo2.png"))))
```


### Holding centre merge

```{r}

holding_centres_join <- holding_centres |> 
  st_transform(st_crs(adm3)) |> 
  st_join(
    adm3
  ) |> 
  filter(!is.na(name)) %>%
  filter(!st_is_empty(.)) %>%
  select(where(~ !all(is.na(.)))) |> 
  select(name, adm1_name, adm1_pcode, adm2_name, adm2_pcode, adm3_name, adm3_pcode, geometry) 

holding_centres_complete <- holding_centres_join |> 
  cbind(
    st_coordinates(holding_centres_join$geometry)
  ) |> 
  clean_names()

```

```{r}
damage_points_20260914 <- damage_points |> 
  rename(
    adm1_name = province, 
    adm2_name = district, 
    adm3_name = municipality
  ) |> 
  rbind(
    holding_centres_complete |> 
      st_drop_geometry() |> 
      mutate(type = "Holding Centre", 
             ownership = NA_character_,
             damage = NA_character_) |> 
      select(adm1_name, adm2_name, adm3_name, 
             name, type, x, y, ownership, damage)
  ) |> 
  mutate_at(vars(adm1_name, adm2_name, adm3_name), 
            ~ str_trim(.x)) |> 
  mutate(adm1_name = ifelse(adm1_name == "Bagamati", "Bagmati", adm1_name), 
         adm2_name = ifelse(adm2_name == "Chitwan", "Chitawan", adm2_name), 
         adm3_name = ifelse(adm3_name == "Ichchhakamana", "Ichchha Kamana", adm3_name)
         ) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode, 
               adm2_name, adm2_pcode, 
               adm3_name, adm3_pcode), 
    by = c("adm1_name", "adm2_name", "adm3_name")
  ) 

damage_points_20260914 |> writexl::write_xlsx("./data/damage_points_20260914.xlsx")

```



# Plotting 

```{r}
consolidated |> 
  filter(!is.na(individuals_reached)) |> 
  filter(municipality == "Bidur" & ward == 2)
```



```{r}
HEX
"#002e6e"
"#004987"
"#0074b7"
"#009edb" -- UN blue
"#64bdea"
"#c5dfef"
"#e3edf6"

"#003425"
"#004d35"
"#006747"
"#338c46"
"#72bf44"
"#cee3a0"
"#e6efd0"

```

## Magnitude and severity mapping 

```{r plotting-functions}
magnitude_plot <- function(tbl, filter_value) {
  
  tbl |> 
    filter(variable == filter_value) |> 
    mutate(variable = str_replace_all(variable, "_", " "),
           variable = str_to_title(variable)) |> 
    mutate(value = ifelse(value == 0, NA_integer_, value)) |> 
    right_join(adm3, 
              by = c("adm2_pcode", "adm3_pcode")) |>
    mutate(adm3_name_label = ifelse(!is.na(value), adm3_name, ""),
           label = ifelse(!is.na(value),
                          as.character(format(round(value, 1), big.mark = ",")), 
                          "")) |>
    replace_na(list(label = "", adm3_name_label = "")) |> 
    st_as_sf() |> 
    ggplot() +
    geom_sf(aes(fill = value), linewidth = .1) +
    geom_sf(data = river, colour = "#e56a54", fill = "#e56a54", alpha = .2) +
    geom_shadowtext(
      aes(x = center_lon, y = center_lat, 
          label = paste0(adm3_name_label, "\n", label)), 
      size = 2, color = "black",  bg.color = "white", bg.r = 0.1) +
    coord_sf(xlim = c(84.3, 85.8), ylim = c(27.63, 28.4), expand = TRUE) +
    scale_fill_gradient(low = "#e3edf6", high = "#002e6e", labels = comma, na.value = "grey97") +
    labs(title = paste0(str_to_title(str_replace_all(filter_value, "_", " "))), 
         fill = paste0(str_to_title(str_replace_all(filter_value, "_", "\n"))), 
         x = "", y = "") +
    theme(plot.subtitle = element_text(margin = margin(b = -2)))

}


severity_plot <- function(tbl, filter_value) {
  
  tbl |> 
    filter(variable == filter_value) |> 
    mutate(value = ifelse(value == 0, NA_integer_, value)) |> 
    right_join(adm3, 
              by = c("adm2_pcode", "adm3_pcode")) |>
    mutate(adm3_name_label = ifelse(!is.na(value), adm3_name, ""),
           label = ifelse(!is.na(value),
                          paste0(round(value * 100, 2), "%"),  
                          "")) |>
    replace_na(list(label = "", adm3_name_label = "")) |> 
    st_as_sf() |> 
    ggplot() +
    geom_sf(aes(fill = value), linewidth = .1) +
    geom_sf(data = river, colour = "#e56a54", fill = "#e56a54", alpha = .2) +
    geom_shadowtext(
      aes(x = center_lon, y = center_lat, 
          label = paste0(adm3_name_label, "\n", label)), 
      size = 2, color = "black",  bg.color = "white", bg.r = 0.1) +
    coord_sf(xlim = c(84.3, 85.8), ylim = c(27.63, 28.4), expand = TRUE) + 
    scale_fill_gradient(low = "#e3edf6", high = "#002e6e", labels = percent, na.value = "grey97")+
    labs(x = "", y = "") + 
    theme(plot.subtitle = element_text(margin = margin(b = -2)))

}
```



```{r magnitude-plots-assembly, fig.height=9}

municipal_long |> 
  magnitude_plot("impacted_population") +
  labs(title = "The Population was Impacted across 61 wards in 20 municipalities", 
       subtitle = "As of 20260909, from the NDRRMA Rapid Disaster Needs Assessment.") +

municipal_long |> 
  magnitude_plot("affected_buildings") + 
  labs(subtitle = "As of 20260909, from the NDRRMA Rapid Disaster Needs Assessment.", 
       title = "7,570 buildings were Impacted across the Damage Corridor") +
  
municipal_long |> 
  magnitude_plot("affected_hectares_agriculture") + 
  labs(subtitle = "As of 20260909, from the NDRRMA Rapid Disaster Needs Assessment.", 
       title = "1,806 Hectares of Agricultural Land were Impacted") +

consolidated |>
  filter(municipality != "Kathmandu") |> 
  filter(disaster_response_plan == "Rasuwa Flood Response") |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  filter(is.finite(individuals_reached)) |> 
  filter(!is.na(adm2_pcode) & !is.na(adm3_pcode)) |> 
  group_by(adm2_pcode, adm3_pcode) |> 
  summarise(individuals_reached = max(individuals_reached, na.rm = TRUE), 
            .groups = "drop") |> 
  mutate(variable = "individuals_reached") |> 
  rename(value = individuals_reached) |> 
  magnitude_plot("individuals_reached") +
  labs(subtitle = "As of 20260911.", 
       title = "Individuals Reached by the Humanitarian Response according to the 5Ws") +
  
  combined_logos +

  plot_layout(ncol = 2, 
              heights = c(10, 10, 1), 
  design = "
AAABBB
CCCDDD
EE####
") + 
  plot_annotation(
    title = "Municipal-level plots of the Magnitude of the Rasuwa Floods Disaster Impacts and the Humanitarian Response", 
    caption = "Sources: Survey Department, Government of Nepal; Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners.", 
    theme = theme(
      plot.title = element_text(size = 20, face = 'bold'))
    )

ggsave("./plots/magnitude_disaster_impact_5ws.png", height = 11.7, width = 16.5, units = "in")
```


```{r severity-plots-assembly, fig.height=9}

municipal_damage_losses |> 
  left_join(
    differences |>
      filter(rdna_affected == 1) |>
      group_by(adm2_pcode, adm3_pcode) |>
      summarise(population_in_affected_wards = sum(projection_2026_population_total, na.rm = TRUE),
                .groups = "drop"), 
    by = c("adm2_pcode", "adm3_pcode")) |> 
  mutate(pc_affected_population = impacted_population_total / population_in_affected_wards) |> 
  select(district, adm2_pcode, municipality, adm3_pcode, value = pc_affected_population) |>
  mutate(variable = "% of Population Affected") |> 
  severity_plot("% of Population Affected") + 
  labs(title = "% of Population Impacted, within Damage Corridor", 
       subtitle = "As of 20260909, from the NDRRMA Rapid Disaster Needs Assessment.", 
       fill = "% of\nPopulation\nAffected") +

municipal_long |> 
  mutate(variable = case_when(
    variable == "pc_affected_buildings" ~ "% of buildings affected, within damage corridor", 
    variable == "pc_affected_hectares" ~ "% of hectares of agricultural land, within damage corridor", 
    TRUE ~ variable
  )) |> 
  severity_plot("% of buildings affected, within damage corridor") + 
  labs(title = "% of Buildings Affected, within Damage Corridor", 
       subtitle = "As of 20260909, from the NDRRMA Rapid Disaster Needs Assessment.",
       fill = "% of\nBuildings\nAffected") +

municipal_long |> 
  mutate(variable = case_when(
    variable == "pc_affected_buildings" ~ "% of buildings affected, within damage corridor", 
    variable == "pc_affected_hectares" ~ "% of hectares of agricultural land, within damage corridor", 
    TRUE ~ variable
  )) |> 
  severity_plot("% of hectares of agricultural land, within damage corridor") + 
  labs(title = "% of Agricultural land affected, within Damage Corridor", 
       subtitle = "As of 20260909, from the NDRRMA Rapid Disaster Needs Assessment.",
       fill = "% of\nAgricultrual\nland\nAffected") +

consolidated |>
  filter(municipality != "Kathmandu") |> 
  filter(disaster_response_plan == "Rasuwa Flood Response") |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  filter(is.finite(individuals_reached)) |> 
  filter(!is.na(adm2_pcode) & !is.na(adm3_pcode)) |> 
  group_by(adm2_pcode, adm3_pcode) |> 
  summarise(individuals_reached = max(individuals_reached, na.rm = TRUE), 
            .groups = "drop") |> 
  right_join(
    differences |> 
      filter(rdna_affected == 1) |> 
      group_by(adm2_pcode, adm3_pcode) |> 
      summarise(population = sum(projection_2026_population_total), 
                .groups = "drop"), 
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  mutate(pc_of_affected_reached = individuals_reached / population, 
         variable = "% of Affected Population Reached by 5W activities") |>
  select(adm2_pcode, adm3_pcode, variable, value = pc_of_affected_reached) |> 
  severity_plot("% of Affected Population Reached by 5W activities") + 
  labs(title = "% of Affected Population Reached by 5W activities", 
       fill = "% of\nPopulation\nReached", 
       subtitle = "As a percentage of the population of affected wards, as of 20260911.") +
  
  combined_logos +

  plot_layout(ncol = 2, 
              heights = c(10, 10, 1), 
  design = "
AAABBB
CCCDDD
EE####
") + 
  plot_annotation(
    title = "Municipal-level plots of the Severity of the Rasuwa Floods Disaster Impacts and the Humanitarian Response", 
    caption = "Sources: Survey Department, Government of Nepal; Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners.", 
    theme = theme(
      plot.title = element_text(size = 20, face = 'bold'))
  )

ggsave("./plots/severity_disaster_impact_5ws.png", height = 11.7, width = 16.5, units = "in")
```


```{r}
consolidated |>
  filter(municipality != "Kathmandu") |> 
  filter(is.finite(individuals_reached)) |> 
  filter(!is.na(adm2_pcode) & !is.na(adm3_pcode)) |> 
  group_by(adm2_pcode, adm3_pcode) |> 
  summarise(individuals_reached = max(individuals_reached, na.rm = TRUE), 
            .groups = "drop") |> 
  right_join(
    differences |> 
      filter(rdna_affected == 1) |> 
      group_by(adm2_pcode, adm3_pcode) |> 
      summarise(population = sum(projection_2026_population_total), 
                .groups = "drop"), 
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  mutate(pc_of_affected_reached = individuals_reached / population, 
         variable = "% of Affected Population Reached by 5W activities") |>
  select(adm2_pcode, adm3_pcode, variable, value = pc_of_affected_reached)
```



## Wards

### Ward differences 

```{r}
differences |> 
  mutate(
    assessment_category = case_when(
      flash_appeal_affected == 1 & rdna_affected == 1 ~ "Both", 
      flash_appeal_affected == 1 & rdna_affected == 0 ~ "Only Flash Appeal", 
      rdna_affected == 1 & flash_appeal_affected == 0 ~ "Only RDNA", 
      TRUE ~ NA_character_
    )
  ) |> 
  right_join(wards, 
             by = c("adm2_pcode", "adm3_pcode", "ward")) |> 
  st_as_sf() |> 
  mutate(ward_label = ifelse(!is.na(flash_appeal_affected == 1 | rdna_affected ==1), 
                             paste0(ward, "\n", format(projection_2026_population_total, big.mark = ",")), 
                             ""), 
         adm3_label = ifelse(adm3_pcode %in% (differences |> distinct(adm3_pcode) |> pull()), 
                             municipality, 
                             "")) |> 
  ggplot() +
  geom_sf(linewidth = .1, alpha = .1, fill = "grey97") +
  geom_sf(data = adm3, alpha = .25, linewidth = .5, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
            mutate(adm3_label = ifelse(adm3_pcode %in% (differences |> distinct(adm3_pcode) |> pull()),
                                       adm3_name,
                                       "")), 
            aes(label = adm3_label)
          ) + 
  geom_sf(aes(fill = assessment_category), alpha = .7, colour = NA) + 
  scale_fill_manual(values = c(
    "Both" = "#0074b7", 
    "Only Flash Appeal" = "#c5dfef", 
    "Only RDNA" = "#338c46"), 
    na.value = "grey97", 
    na.translate = FALSE) +
  geom_sf(data = river, colour = "#e56a54", fill = "#e56a54", alpha = .5) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates",
      size = 2, color = "black",  bg.color = "white", bg.r = 0.1) +
    coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.4), expand = TRUE) + 
  labs( x = "", y = "", 
       fill = "") +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    title = "Affected wards and their populations, mentioned in the Flash Appeal and the Rapid Disaster Needs Assessment", 
    subtitle = "Ward numbers and their 2026 population projections are labelled.", 
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners.", 
    theme = theme(
      plot.title = element_text(size = 20, face = 'bold'))
  )

ggsave("./plots/affected_wards.png", height = 11.7, width = 16.5, units = "in")  
```



### Wards and points


```{r}
differences |> 
  mutate(
    rdna_affected = ifelse(rdna_affected == 1, "Affected", NA_character_)) |> 
  right_join(wards, 
             by = c("adm2_pcode", "adm3_pcode", "ward")) |> 
  st_as_sf() |> 
  mutate(ward_label = ifelse(!is.na(rdna_affected == "Affected"), 
                             paste0(ward, "\n", format(projection_2026_population_total, big.mark = ",")), 
                             ""), 
         adm3_label = ifelse(adm3_pcode %in% (differences |> distinct(adm3_pcode) |> pull()), 
                             municipality, 
                             "")) |> 
  ggplot() +
  # Ward boundaries
  geom_sf(linewidth = .1, alpha = .1, fill = "grey97") +
  # Municipality boundaries
  geom_sf(data = adm3, alpha = .25, linewidth = .5, colour = "grey70", fill = NA) +
  # Municipality names
  geom_sf_text(data = adm3 |> 
            mutate(adm3_label = ifelse(adm3_pcode %in% (differences |> distinct(adm3_pcode) |> pull()),
                                       adm3_name,
                                       "")), 
            aes(label = adm3_label)
          ) + 
  geom_sf(data = river, colour = "#002e6e", fill = "#002e6e", alpha = .5) +
  # Damage points 
  geom_point(data = damage_points, 
             aes(x = x, y = y, colour = type)) +
  geom_label_repel(data = damage_points, 
                aes(x = x, y = y, label = name),
                size = 1.5) +
  # geom_shadowtext(data = damage_points, 
  #                 aes(label = name, x = x, y = y),
  #     size = 2, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = 
                        c("Hydropower" = "#ffc800", 
                          "Medical Facility" = "#e56a54", 
                          "School" = "#72bf44")
  ) +
  coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.4), expand = TRUE) + 
  labs( x = "", y = "", 
       fill = "") +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    title = "Affected wards and Key Infrastructure Affected", 
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners.", 
    theme = theme(
      plot.title = element_text(size = 20, face = 'bold'))
  )

ggsave("./plots/affected_wards_infrastructure.png", height = 11.7, width = 16.5, units = "in")  

```



# Ward

## Population

```{r}
ward_populations <- differences |> 
      select(adm3_pcode, ward, affected_20260923) |> 
  left_join(read_csv("./data/population_projections_2026_affected_wards_flat.csv") |> 
              select(adm3_pcode, ward, population_2026 = projection_2026_population_total), 
            by = c("adm3_pcode", "ward")) |> 
  left_join(
    consolidated |> 
      filter(individuals_reached > 0) |> 
      group_by(adm3_pcode, ward) |> 
      summarise(max_individuals_reached = max(individuals_reached, na.rm = TRUE), 
                individuals_reached = sum(individuals_reached, na.rm = TRUE)), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(
    census_flat |> 
      select(population_2021 = population_total, adm3_pcode, ward),
    by = c("adm3_pcode", "ward")
  ) |> 
  # This is because we don't have the countrywide tables
  mutate(population = ifelse(!is.na(population_2026), population_2026, population_2021),
         affected = ifelse(affected_20260923 == 1, "Affected", NA_character_), 
         category = case_when(affected == "Affected" ~ "Affected", 
                              is.na(affected) & !is.na(individuals_reached) ~ "Outside") 
         population = ifelse(!is.na(affected), population, NA_real_)) |>
  right_join(
    wards |> 
      select(-population), 
    by = c("adm3_pcode", "ward")
  )  |> 
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(affected), 
           ward_label,
           ""
         )) |> 
  st_as_sf() |> 
  ggplot() +
  # Ward populations and affected wards
  geom_sf(aes(fill = population), linewidth = .1) +
  geom_sf(data = adm3, alpha = .25, linewidth = .5, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = comma,
                          na.value = "grey99") +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  coord_sf(xlim = c(84.5, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       title = "Ward Populations in Flood-affected areas",
       subtitle = "Ward numbers listed.",
       fill = "Ward\nPopulation") + 
  theme(plot.title = element_text(size = 20, face = "bold")) + 
  guides(fill = guide_colorbar(order = 1), 
         colour = guide_legend(order = 2)) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: National Population and Housing Census 2021; 2026 Ward-level Population Projections, National Statistics Office, NDRRMA Rapid Disaster Needs Assessment."
  )

ggsave("./plots/ward_populations.png", ward_populations, height = 11.7, width = 16.5, units = "in") 
```


### Reached gaps

```{r}
ward_gaps <- consolidated |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  filter(is.finite(individuals_reached)) |> 
  filter(ward < 20) |> 
  group_by(adm3_pcode, ward) |> 
  summarise(individuals_reached = max(individuals_reached, na.rm = TRUE)) |> 
  full_join(
    differences |> 
      select(adm3_pcode, ward, flash_appeal_affected, rdna_affected), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(read_csv("./data/population_projections_2026_affected_wards_flat.csv") |> 
              select(adm3_pcode, ward, population_2026 = projection_2026_population_total), 
            by = c("adm3_pcode", "ward")) |> 
  left_join(
    census_flat |> 
      select(population_2021 = population_total, adm3_pcode, ward),
    by = c("adm3_pcode", "ward")
  ) |> 
  # This is because we don't have the countrywide tables
  mutate(population = ifelse(!is.na(population_2026), population_2026, population_2021),
         pc_reached = individuals_reached / population, 
         flash_appeal_affected = ifelse(flash_appeal_affected == 1, "Affected", NA_character_)) |>
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> 
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(flash_appeal_affected) | individuals_reached > 0, 
           ward_label,
           ""
         )) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = pc_reached), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = percent, na.value = "grey97") +
    # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  geom_sf(aes(colour = flash_appeal_affected), fill = NA, linewidth = .75) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "% of Ward\nPopulation\nReached",
       colour = "Flash\nAppeal", 
       title = "Percentage of Ward Population Reached by 5W Activities in Flash Appeal Areas (No Double Counting)", 
       subtitle = "Ward-level reached is the SUM of any activity in the ward; 33.5% of beneficiary frequencies were reported at ward level.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners."
  )

ggsave("./plots/ward_gaps.png", ward_gaps, height = 11.7, width = 16.5, units = "in") 
  
    
```

### Sum individuals

```{r}
ward_reached_sum <- consolidated |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  filter(is.finite(individuals_reached)) |> 
  filter(ward < 20) |> 
  group_by(adm3_pcode, ward) |> 
  summarise(individuals_reached = sum(individuals_reached, na.rm = TRUE)) |> 
  full_join(
    differences |> 
      select(adm3_pcode, ward, affected_20260923, rdna_affected), 
    by = c("adm3_pcode", "ward")
  ) |> 
  # This is because we don't have the countrywide tables
  mutate(affected_20260923 = ifelse(affected_20260923 == 1, "Affected", NA_character_)) |>
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> 
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(affected_20260923) | individuals_reached > 0, 
           ward_label,
           ""
         )) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = individuals_reached), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = comma, na.value = "grey99") +
    # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  geom_sf(aes(colour = affected_20260923), fill = NA, linewidth = .75) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.5, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "Beneficiary\nFrequencies",
       colour = "", 
       title = "Beneficiary Frequencies Reached by 5W Activities in Flash Appeal Areas (With Double Counting)", 
       subtitle = "33% of beneficiary frequencies were reported at ward level. Ward numbers listed.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  guides(fill = guide_colorbar(order = 1), 
         colour = guide_legend(order = 2)) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners; 5Ws 20260923."
  )

ggsave("./plots/ward_reached_sum.png", ward_reached_sum, height = 11.7, width = 16.5, units = "in")  
```

### % of ward population

```{r}
ward_gaps <- consolidated |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  filter(is.finite(individuals_reached)) |> 
  filter(ward < 20) |> 
  group_by(adm3_pcode, ward) |> 
  summarise(individuals_reached = max(individuals_reached, na.rm = TRUE)) |> 
  full_join(
    differences |> 
      select(adm3_pcode, ward, flash_appeal_affected, rdna_affected), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(read_csv("./data/population_projections_2026_affected_wards_flat.csv") |> 
              select(adm3_pcode, ward, population_2026 = projection_2026_population_total), 
            by = c("adm3_pcode", "ward")) |> 
  left_join(
    census_flat |> 
      select(population_2021 = population_total, adm3_pcode, ward),
    by = c("adm3_pcode", "ward")
  ) |> 
  # This is because we don't have the countrywide tables
  mutate(population = ifelse(!is.na(population_2026), population_2026, population_2021),
         pc_reached = individuals_reached / population, 
         flash_appeal_affected = ifelse(flash_appeal_affected == 1, "Affected", NA_character_)) |>
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> 
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(flash_appeal_affected) | individuals_reached > 0, 
           ward_label,
           ""
         )) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = pc_reached), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = percent, na.value = "grey97") +
    # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  geom_sf(aes(colour = flash_appeal_affected), fill = NA, linewidth = .75) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "% of Ward\nPopulation\nReached",
       colour = "Flash\nAppeal", 
       title = "Percentage of Ward Population Reached by 5W Activities in Flash Appeal Areas (No Double Counting)", 
       subtitle = "Ward-level reached is the SUM of any activity in the ward; 33.5% of beneficiary frequencies were reported at ward level.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners."
  )

ggsave("./plots/ward_gaps.png", ward_gaps, height = 11.7, width = 16.5, units = "in")  
```

```{r}
ward_gaps_sum <- consolidated |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  filter(is.finite(individuals_reached)) |> 
  filter(ward < 20) |> 
  group_by(adm3_pcode, ward) |> 
  summarise(individuals_reached = sum(individuals_reached, na.rm = TRUE)) |> 
  full_join(
    differences |> 
      select(adm3_pcode, ward, flash_appeal_affected, rdna_affected), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(read_csv("./data/population_projections_2026_affected_wards_flat.csv") |> 
              select(adm3_pcode, ward, population_2026 = projection_2026_population_total), 
            by = c("adm3_pcode", "ward")) |> 
  left_join(
    census_flat |> 
      select(population_2021 = population_total, adm3_pcode, ward),
    by = c("adm3_pcode", "ward")
  ) |> 
  # This is because we don't have the countrywide tables
  mutate(population = ifelse(!is.na(population_2026), population_2026, population_2021),
         pc_reached = individuals_reached / population, 
         flash_appeal_affected = ifelse(flash_appeal_affected == 1, "Affected", NA_character_)) |>
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> 
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(flash_appeal_affected) | individuals_reached > 0, 
           ward_label,
           ""
         )) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = pc_reached), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  geom_sf(aes(colour = flash_appeal_affected), fill = NA, linewidth = .75) +
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = percent, na.value = "grey98") +
    # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "% of Ward\nPopulation\nReached",
       colour = "Flash\nAppeal", 
       title = "Percentage of Ward Population Reached by 5W Activities in Flash Appeal Areas (No Double Counting)", 
       subtitle = "To avoid double counting, ward-level reached is the MAX of any activity in the ward; 33.5% of beneficiary frequencies were reported at ward level.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners."
  )

ggsave("./plots/ward_gaps_sum.png", ward_gaps_sum, height = 11.7, width = 16.5, units = "in")  
```

### Sectors

```{r}
ward_summary <- read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv") |> 
  select(-different) |> 
  left_join(impacted_buildings |> 
      select(adm3_pcode, ward, impacted_buildings), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(
    read_csv("./data/nepal_census2021_ward_level_household_tables_bagmati_gandaki_flat.csv") |> 
      select(adm3_pcode, ward, 
             total_households 
             ), 
    by = c("adm3_pcode", "ward")
  ) |>
  left_join(
    consolidated |> 
    filter(response_modality != "Awareness/Advocacy") |> 
    filter(!is.na(sector)) |> 
    mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
           sector = ifelse(str_detect(sector, "Health|Nutrition"), "Health & Nutrition", sector)) |> 
    filter(ward < 20 & individuals_reached > 0) |> 
    group_by(adm3_pcode, ward, sector) |> 
    summarise(individuals_reached = sum(individuals_reached), .groups = "drop") |> 
    pivot_wider(names_from = sector, 
                values_from = individuals_reached, 
                names_glue = "{sector}_{.value}"), 
    by = c("adm3_pcode", "ward")
  ) |> 
  clean_names() |> 
  rowwise() |> 
  mutate(num_sectors = 
           sum(!is.na(across(c(food_security_individuals_reached:logistics_individuals_reached)))), 
         num_sectors = ifelse(num_sectors == 0, NA_real_, num_sectors)) |> 
  ungroup() 
```

```{r}
ward_sectors <- ward_summary |>
  # This is because we don't have the countrywide tables
  mutate(affected_20260923 = ifelse(affected_20260923 == 1, "Affected", NA_character_)) |>
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> 
  mutate(ward_label = as.character(num_sectors), 
         ward_label = ifelse(
           !is.na(affected_20260923), 
           num_sectors,
           ""
         )) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = num_sectors), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = comma, na.value = "grey99") +
  # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  geom_sf(aes(colour = affected_20260923), fill = NA, linewidth = .75) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.5, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "Number\nof Sectors",
       colour = "Flash\nAppeal", 
       title = "Number of Sectors/Clusters present in Flash Appeal Areas", 
       subtitle = "33% of beneficiary frequencies were reported at ward level. Number of sectors listed.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  guides(fill = guide_legend(order = 1), 
         colour = guide_legend(order = 2)) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners; 5Ws 20260921."
  )

ggsave("./plots/ward_sectors.png", ward_sectors, height = 11.7, width = 16.5, units = "in")  
```

## Clustering


```{r}
to_cluster <- census_flat |> 
  mutate(improved_drinking_water = drinking_water_tap_piped_within_premises +
           drinking_water_tap_piped_outside_premises +
           drinking_water_tubewell_handpump +
           drinking_water_covered_well_kuwa, 
         no_toilet_public_toilet = toilet_no_toilet + toilet_public, 
         house_quality_inadequate_least_adequate_pc = house_quality_inadequate_pc + house_quality_least_adequate_pc
           ) |>
  mutate(unimproved_sanitation_pc = no_toilet_public_toilet / total_households * 100, 
         unimproved_drinking_water_pc = (total_households - improved_drinking_water) / total_households * 100) |> 
  select(
    adm3_pcode, ward,
    # population_total, 
    population_density, 
    sex_ratio, 
    average_household_size, 
    total_dependency_ratio, 
    population_pc_rural, 
    disability_prevlance_rate, 
    agricultural_employment_pc_total, 
    wealth_quintile_poorest_quintile_pc, 
    house_quality_inadequate_least_adequate_pc,
    unimproved_sanitation_pc, 
    unimproved_drinking_water_pc
  ) |> 
  right_join(
    differences |>
      left_join(
        impacted_buildings |>
          select(impacted_buildings, adm3_pcode, ward),
        by = c("adm3_pcode", "ward")) |> 
      select(adm3_pcode, ward, 
             population_total = projection_2026_population_total, 
             impacted_buildings), 
    by = c("adm3_pcode", "ward")
  ) |> 
  replace_na(list(impacted_buildings = 0))
```

```{r}
# k-means clustering and output
set.seed(123)

km <- to_cluster |>
  select(-adm3_pcode, -ward) |>
  mutate_at(
    vars(population_density:impacted_buildings), 
    ~ range_wna(.x)
  ) |> 
  kmeans(4, nstart = 25)

clustered <- to_cluster |> 
  cbind(cluster = km$cluster) |> 
  mutate(
    cluster = case_when(
      cluster == 4 ~ "A", 
      cluster == 3 ~ "B",
      cluster == 2 ~ "C", 
      cluster == 1 ~ "D"
    )
  )
```



```{r}
wards_clustered <- clustered |>
  # Doing this prevents Bandipur from coming up 
  right_join(
    differences |> 
      filter(affected_20260923 == 1) |> 
      select(ward, adm3_pcode, affected_20260923), 
    by = c("adm3_pcode", "ward")
  ) |> 
  mutate(affected_20260923 = ifelse(affected_20260923 == 1, "Affected", NA_character_)) |>
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(cluster),
           ward_label,
           ""
         )) |> 
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = cluster), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  scale_fill_manual(values = c(
    "A" = "#ffc800",
    "B" = "#cf9220", 
    "C" = "#763f98", 
    "D" = "#bd8cbf"), 
    na.value = "grey97", 
    na.translate = FALSE
    ) +
  # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  # geom_sf(aes(colour = affected_20260923), fill = NA, linewidth = .75) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  # scale_colour_manual(values = c("Affected" = "#e56a54"), 
  #    na.value = "grey80", 
  #    na.translate = FALSE) + 
  coord_sf(xlim = c(84.5, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "Group",
       colour = "Flash\nAppeal",
       title = "Affected wards by Sub-context", 
       subtitle = "K-means clustering was used to split the affected wards into 4 groups based on flood damage and demographic and vulnerability indicators. Ward numbers listed.\nA: Highly-impacted entirely rural. B: Highly-impacted entirely urban. C: Less impacted, poorest areas. D: Less impacted.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  guides(fill = guide_legend(order = 1), 
         colour = guide_legend(order = 2)) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners."
  )

ggsave("./plots/wards_clustered.png", wards_clustered, height = 11.7, width = 16.5, units = "in")  
```





## Assessments

```{r}
register <- read_xlsx("./data/Nepal - Assessment registry - Rasuwa Flood.xlsx", skip = 3) |> 
  setNames(c("lead_organisation", "participating_organisation", 
             "assessment", "description", "sector", 
             "province", "district", "municipality", "ward", 
             "representative_at_level", "status", "status_update", 
             "data_collection_method", "availability_report", "email_contact", 
             "permission_public", "report_link", "dashboard_link", 
             "comments"))

register |> 
  mutate(sector = str_remove_all(sector, "Protection / Child Protection|Protection / Child Protection, Protection / GBV,|Health / SRH,|Protection / GBV,|Multi-Sector")) |> 
  separate_longer_delim(sector, delim = "/") |> 
  separate_longer_delim(sector, delim = ",") |> 
  filter(sector != "") |> 
  count(sector)

assessment_locations <- register |>   
  mutate(municipality = ifelse(!is.na(district) & is.na(municipality), 
                               "unspecified", 
                               municipality)) |> 
  separate_longer_delim(district, delim = ",") |> 
  separate_longer_delim(municipality, delim = ",") |> 
  mutate_at(vars(district, municipality), ~ str_trim(.x)) |> 
  left_join(
    nepal_admin |> 
      distinct(adm2_name, adm2_pcode, adm3_name, adm3_pcode), 
    by = c("district" = "adm2_name", "municipality" = "adm3_name")
  )  |> 
  filter(district != "Kathmandu" & municipality != "Tarakeshwor") |> 
  mutate(adm2_pcode = case_when(
    district == "Chitawan" ~ "NP0335", 
    district == "Dhading" ~ "NP0330", 
    district == "Gorkha" ~ "NP0436", 
    district == "Nuwakot" ~ "NP0328", 
    district == "Rasuwa" ~ "NP0329", 
    district == "Tanahu" ~ "NP0440",
    TRUE ~ district
  )) |> 
  filter(!is.na(adm3_pcode) | municipality == "unspecified")


```


```{r}
assessment_map <- assessment_locations |>  
  count(district, municipality, adm2_pcode, adm3_pcode) |> 
  right_join(
    adm3, 
    by = "adm3_pcode"
  ) |> 
  st_as_sf() |> 
  ggplot() +
  geom_sf(data = assessment_locations |>
            count(district, municipality, adm2_pcode, adm3_pcode) |>
            filter(municipality == "unspecified") |>  
            right_join(adm2, by = "adm2_pcode") |> 
            st_as_sf(), 
          aes(fill = n), linewidth = .7, colour = "grey80", alpha = .5) + 
  geom_sf(aes(fill = n), linewidth = .5, colour = "grey60", alpha =.5) +
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = comma, na.value = NA) +
  geom_sf_text(data = adm2, aes(label = adm2_name), colour = "grey50", alpha = .7, size = 8) +
  geom_sf_text(aes(label = municipality), colour = "grey30", alpha = .85, size = 6) +
  # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  scale_colour_manual(na.value = "white") + 
  coord_sf(xlim = c(84.2, 85.75), ylim = c(27.5, 28.4)) + 
  labs(title = "Number of Needs Assessments by Location",
       subtitle = "Some assessments in the registry only mentioned the whole district instead of specifying municipalities", 
       x = "", y = "", 
       fill = "Number of\nAssessments") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners; Assessment Registry 20260920."
  )

ggsave("./plots/assessment_map.png", assessment_map, height = 11.7, width = 16.5, units = "in")   
```




## Impacted buildings

```{r}
impacted_buildings |> 
    left_join(wards_joined, 
    by = c("adm2_pcode", "adm3_pcode", "ward")) |>
    filter(adm2_en == district_name) |>
    mutate(ward_label = ifelse(!is.na(impacted_buildings), 
                                      paste0(ward, "\n", impacted_buildings))) |> 
    st_as_sf() |> 
    ggplot() +
    geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
    geom_sf_text(data = adm3 |> filter(adm2_name == district_name), 
              aes(label = adm3_name),
              alpha = .5
            ) +
    # Ward populations and affected wards
    geom_sf(aes(colour = rdna, fill = impacted_buildings), linewidth = .5, alpha = .8) +
    # River
    geom_sf(data = river, colour = "#002e6e", fill = "#002e6e", alpha = .6) +
    # Settlements
    geom_sf(data = settlements_holding_centre |> filter(adm2_en == district_name) |>  
              mutate(fclass = str_to_title(fclass), 
                     fclass = fct_relevel(fclass, c("Hamlet", "Village", "Suburb", "Town", 
                                                    "Holding Centre"))), 
            aes(geometry = geometry, shape = fclass), colour = "#ffc800", alpha = .5) +
    geom_text(data = capitals |> filter(district == district_name), aes(x = x, y = y, label = name), 
            size = 2.5, colour = "#ed1847", alpha = .8) +
    scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey97", 
      na.translate = FALSE) +
    scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = comma) +
    scale_shape_manual(values = c("Hamlet" = 20, 
                                  "Village" = 16, 
                                  "Suburb" = 15, 
                                  "Town" = 17, 
                                  "Holding Centre" = 7)) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  # coord_sf(xlim = c(85.1, 85.8), ylim = c(27.95, 28.4), expand = TRUE) +
  labs(x = "", y = "", 
       title = paste0("Impacted buildings in ", district_name), 
      # subtitle = "1,779 buildings impacted in Rasuwa. District Headqaurters labelled in red.",
      # Don't feel like making the subtitle programmatic
       shape = "Settlement\nType",
       fill = "Impacted\nBuildings", 
       colour = "RDNA", 
       caption = "Source: NDRRMA Rapid Disaster Needs Assessment") +
    guides(fill = guide_colorbar(override.aes = list(alpha = 1),
                                 order = 1), 
           shape = guide_legend(override.aes = list(alpha = 1),
                                order = 2), 
           colour = guide_legend(order = 3))
```

```{r}
consolidated |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  mutate(has_ward = ifelse(ward < 20 & !is.na(ward), "yes", "no")) |> 
  group_by(has_ward) |> 
  summarise(individuals_reached = sum(individuals_reached, na.rm = TRUE))  %>%
  {sum(.$individuals_reached, na.rm = TRUE)}
```

```{r}
affected_municipalities_17 |> glimpse()

differences |>
  filter(affected_20260923 == 1) |> 
  select(adm3_pcode, ward, affected_20260923) |> 
  mutate(affected_20260923 = ifelse(affected_20260923 == 1, "Affected", NA_character_)) |> 
  left_join(
    wards,
    by = c("adm3_pcode", "ward")
  )
```

## Municipal

Municipal-level analyses are not helpful for operational-level planning or advocacy purposes. 

Additionally, a municipality is too large of an administrative area for this response, which is localised around the affected wards in the damage corridor along the river. 

```{r}
municipal_max <- tribble(
  ~district, ~municipality, ~individuals_reached,
"Rasuwa",	"Aamachhodingmo",	4020,
"Rasuwa",	"Gosaikunda",	10178,
"Rasuwa",	"Kalika",	1948,
"Rasuwa",	"Uttargaya",	6172,
"Nuwakot",	"Belkotgadhi",	1665,
"Nuwakot",	"Bidur",	20148,
"Nuwakot",	"Kispang",	4293,
"Nuwakot",	"Tarakeshwor",	1408,
"Dhading",	"Benighat Rorang",	5000,
"Dhading",	"Gajuri",	2454,
"Dhading",	"Galchhi",	5899,
"Dhading",	"Siddhalek",	1078
) |> 
  left_join(
    nepal_admin |> 
      distinct(adm2_name, adm2_pcode, adm3_name, adm3_pcode), 
    by = c("district" = "adm2_name", 
           "municipality" = "adm3_name")
  ) |> 
  full_join(
    affected_municipalities_17 |> 
      select(adm3_pcode, estimated_affected_population), 
    by = "adm3_pcode"
  ) |> 
  right_join(
    adm3, 
    by = "adm3_pcode")  |>
  mutate(affected = ifelse(!is.na(estimated_affected_population), 
                                        "Affected", 
                                        NA_character_)) |> 
  mutate(mun_label = case_when(
    !is.na(individuals_reached) ~ paste0(adm3_name, "\n", comma(individuals_reached)),
    is.na(individuals_reached) & !is.na(affected) ~ adm3_name, 
    TRUE ~ ""
  )) |> 
  st_as_sf() |> 
  ggplot() +
  # geom_sf(data = differences |>
  #           filter(affected_20260923 == 1) |>
  #           select(adm3_pcode, ward, affected_20260923) |>
  #           mutate(affected_20260923 = ifelse(affected_20260923 == 1, "Affected", NA_character_)) |>
  #           left_join(wards, by = c("adm3_pcode", "ward")) |> 
  #           st_as_sf(),
  #         aes(colour = affected_20260923), fill = NA, linewidth = .5, alpha =.7
  # ) +
  geom_sf(aes(fill = individuals_reached), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_shadowtext(aes(label = mun_label,
                     geometry = geometry), 
      stat = "sf_coordinates", 
      size = 3, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = comma, 
                        na.value = "grey99") +
  geom_sf(aes(colour = affected), fill = NA, linewidth = .75) +
    # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.3, 85.75), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "Individuals\nReached",
       colour = "", 
       title = "Number of Individuals Reached by Municipality (No Double Counting)", 
       subtitle = "To avoid double counting, municipal-level reached is the maximum of any of the activity totals in each municipality, following OCHA's methodology.") +
  theme(plot.title = element_text(size = 18, face = "bold")) +
    guides(fill = guide_colorbar(order = 1), 
         colour = guide_legend(order = 2)) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners."
  )

ggsave("./plots/municipal_max.png", municipal_max, height = 10.5, width = 16.5, units = "in")  
```






```{r}
municipal_gaps_max <- tribble(
  ~district, ~municipality, ~individuals_reached,
"Rasuwa",	"Aamachhodingmo",	4020,
"Rasuwa",	"Gosaikunda",	10178,
"Rasuwa",	"Kalika",	1948,
"Rasuwa",	"Uttargaya",	6172,
"Nuwakot",	"Belkotgadhi",	1665,
"Nuwakot",	"Bidur",	20148,
"Nuwakot",	"Kispang",	4293,
"Nuwakot",	"Tarakeshwor",	1408,
"Dhading",	"Benighat Rorang",	5000,
"Dhading",	"Gajuri",	2454,
"Dhading",	"Galchhi",	5899,
"Dhading",	"Siddhalek",	1078
) |> 
  left_join(
    nepal_admin |> 
      distinct(adm2_name, adm2_pcode, adm3_name, adm3_pcode), 
    by = c("district" = "adm2_name", 
           "municipality" = "adm3_name")
  ) |> 
  full_join(
    affected_municipalities_17 |> 
      select(adm3_pcode, estimated_affected_population), 
    by = "adm3_pcode"
  ) |> 
  left_join(
    census_flat |> 
      group_by(adm3_pcode) |> 
      summarise(population_total = sum(population_total), 
                by = "adm3_pcode")
  ) |> 
  mutate(affected = ifelse(!is.na(estimated_affected_population), 
                                        "Affected", 
                                        NA_character_)) |> 
  replace_na(list(individuals_reached = 0)) |> 
  mutate(pc_reached_of_affected = case_when(
    !is.na(estimated_affected_population) ~ individuals_reached / estimated_affected_population, 
    is.na(estimated_affected_population) & !is.na(individuals_reached) ~ 1, 
    TRUE ~ NA_real_), 
    pc_reached_total_pop = individuals_reached / population_total, 
    pc_reached_total_pop = ifelse(pc_reached_total_pop == 0, NA_real_, pc_reached_total_pop)) |> 
  right_join(
    adm3, 
    by = "adm3_pcode")  |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = pc_reached_total_pop), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_shadowtext(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha") | 
                          adm3_name == "Kathmandu"),
                 aes(label = adm3_name,
                     geometry = geometry), 
      stat = "sf_coordinates", 
      size = 4, color = "black",  bg.color = "white", bg.r = 0.1) +
  geom_sf(aes(colour = affected), fill = NA, linewidth = .75) +
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = percent, na.value = "grey99") +
    # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.3, 85.75), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "% of Municipal\nPopulation\nReached",
       colour = "", 
       title = "Percentage of Municipal Population Reached by 5W Activities in Flood-Affected Areas (No Double Counting)", 
       subtitle = "To avoid double counting, municipal-level reached is the MAX of any activity in the municipality; this plot depicts this as a percentage of the total municipal population ") +
  theme(plot.title = element_text(size = 18, face = "bold")) +
  guides(fill = guide_colorbar(order = 1), 
         colour = guide_legend(order = 2)) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners."
  )

ggsave("./plots/municipal_gaps_max.png", municipal_gaps_max, height = 10.5, width = 16.5, units = "in")  
  
```

## Humanitarian snapshot map


```{r}

impacted_buildings <- municipal_damage_losses |> 
  select(district:adm3_pcode, 
         impacted_buildings) |> 
  filter(!is.na(impacted_buildings)) |> 
  left_join(
    adm3, 
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  select(adm3_name, adm3_pcode, x = center_lon, y = center_lat, impacted_buildings)

floods_bbox_sf <- st_bbox(c(xmin = 84.3, xmax = 85.8, ymin = 27.5, ymax = 29), 
                       crs = st_crs(4326)) |> 
  st_as_sfc()

floods_topo <- get_tiles(floods_bbox_sf, provider = "Esri.WorldShadedRelief", zoom = 11)

impacted_buildings_map <- impacted_buildings |>
  ggplot() + 
  geom_spatraster_rgb(data = floods_topo, alpha = .2) + 
  # Municipality boundaries
  geom_sf(data = adm3 |> 
            filter(adm2_name %in% c("Chitawan", "Dhading", "Gorkha", "Nuwakot", 
                                    "Rasuwa", "Tanahu")),
                   alpha = .25, linewidth = .5, colour = "grey70", fill = NA) +
  # Municipality names
  geom_sf_text(data = adm3 |> 
            mutate(adm3_label = ifelse(adm3_pcode %in% (impacted_buildings |> distinct(adm3_pcode) |> pull()),
                                       adm3_name,
                                       "")), 
            aes(label = adm3_label), 
            colour = "grey20", 
            alpha = .5, 
            size = 4, 
            nudge_x = -0.03, nudge_y = -0.02
          ) + 
  geom_sf(data = river, colour = "#002e6e", fill = "#002e6e", alpha = .6) +
  geom_point(
    aes(x = x, y = y, size = impacted_buildings), 
    colour = "#e56a54", 
    alpha = .7
  ) + 
  scale_size_continuous(range = c(1, 10), labels = comma) +
  coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.4), 
           expand = FALSE,
           datum = st_crs(floods_bbox_sf)) +
  theme_void() + 
  labs(size = "Impacted\nbuildings", 
       title = "NEPAL | Buildings Impacted by the Rasuwa-Trishuli Floods") +
  guides(size = guide_legend(override.aes = list(alpha = .7))) + 
  theme(legend.position = c(0.92, 0.17), 
        plot.title = element_text(face = "bold"))

```

```{r}
minimap <- adm3 |> 
  st_transform(st_crs(4326)) |> 
  ggplot() + 
  geom_sf(color = NA) + 
  geom_rect(aes(xmin = 84.4, xmax = 85.6, ymin = 27.63, ymax = 28.35), 
            color = "#ed1847", 
            fill = NA,      # Keeps the inside transparent
            linewidth = .7) + 
  theme_void() + 
  theme(
    panel.border = element_rect(fill = NA, color = "black", linewidth = 1),
    plot.background = element_rect(fill = "white", color = NA)
  )
```



```{r}
combined_map <- ggdraw() +
  draw_plot(impacted_buildings_map) +  # Main map fills the whole canvas by default
  draw_plot(minimap, 
    x = 0.05,    # Distance from left border (0 to 1)
    y = 0.65,    # Distance from bottom border (0 to 1)
    width = 0.3,  # Relative width of the minimap (30% of canvas)
    height = 0.3  # Relative height of the minimap (30% of canvas)
  ) + 
  canvas(8, 6)

save_ggplot(combined_map, "./plots/snapshot_map.png")
```


# Operational presence

```{r}
consolidated |> 
  filter(!is.na(ward)) |>
  filter(!is.na(adm3_pcode)) |> 
  pivot_longer(cols = lead_agency:implementing_partner, 
               names_to = "agency_role", 
               values_to = "agency") |> 
  group_by(district, adm2_pcode, municipality, adm3_pcode, ward) |> 
  summarise(num_agencies = n_distinct(agency), 
            .groups = "drop") |> 
  full_join(
      read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv") |> 
        select(-different, -projection_2026_population_total), 
      by = c("district", "adm2_pcode", "municipality", "adm3_pcode", "ward")
  ) |>
  replace_na(
    list(num_agencies = 0, 
         flash_appeal_affected = 0, 
         rdna_affected = 0, 
         ndrrma_new = 0)
  ) |> 
  left_join(proj_flat |> 
              select(adm3_pcode, ward, projection_2026_population_total), 
            by = c("adm3_pcode", "ward")
            ) |> 
  mutate(category = case_when(
    ndrrma_new == 1 & rdna_affected == 1 ~ "Both", 
    rdna_affected == 1 & ndrrma_new == 0 ~ "Only RDNA", 
    ndrrma_new == 1 & rdna_affected == 0 ~ "Only New Map", 
    TRUE ~ NA_character_)) |> 
  count(category)


```




```{r}
operational_presence <- consolidated |> 
  filter(!is.na(ward)) |>
  filter(!is.na(adm3_pcode)) |> 
  pivot_longer(cols = lead_agency:implementing_partner, 
               names_to = "agency_role", 
               values_to = "agency") |> 
  group_by(district, adm2_pcode, municipality, adm3_pcode, ward) |> 
  summarise(num_agencies = n_distinct(agency), 
            .groups = "drop") |> 
  full_join(
      read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv") |> 
        select(-different, -projection_2026_population_total), 
      by = c("district", "adm2_pcode", "municipality", "adm3_pcode", "ward")
  ) |>
  replace_na(
    list(num_agencies = 0, 
         flash_appeal_affected = 0, 
         rdna_affected = 0, 
         ndrrma_new = 0)
  ) |> 
  left_join(proj_flat |> 
              select(adm3_pcode, ward, projection_2026_population_total), 
            by = c("adm3_pcode", "ward")
            ) |> 
  mutate(category = case_when(
    ndrrma_new == 1 & rdna_affected == 1 ~ "New Map\nand\nRDNA", 
    rdna_affected == 1 & ndrrma_new == 0 ~ "Only RDNA", 
    ndrrma_new == 1 & rdna_affected == 0 ~ "Only New Map", 
    TRUE ~ NA_character_)) |> 
  mutate(flash_appeal_affected = ifelse(flash_appeal_affected == 1, "Affected", NA_character_)) |> 
  mutate(ward_label = ifelse(num_agencies > 0, num_agencies, "")) |> 
 right_join(
   wards, 
   by = c("adm3_pcode", "ward")
 ) |> 
  st_as_sf() |>
  ggplot() + 
  geom_sf(aes(fill = category), alpha = .8) +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  scale_fill_manual(values = c(
    "New Map\nand\nRDNA" = "#009edb",
    "Only RDNA" = "#72bf44", 
    "Only New Map" = "#e3edf6"), 
    na.value = "grey97", 
    na.translate = FALSE
    ) +
  geom_sf(aes(colour = flash_appeal_affected), fill = NA, linewidth = .75) +
  # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.35)) +
  labs(x = "", y = "", 
       fill = "",
       colour = "Flash\nAppeal",
       title = "Agency Presence in Affected Wards by Flash Appeal, NDRRMA RDNA and New NDRRMA Map", 
       subtitle = "Number of Agencies listed.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  guides(fill = guide_legend(order = 1, 
                             override.aes = list(size = 1)), 
         colour = guide_legend(order = 2)) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners."
  )

ggsave("./plots/operational_presence.png", operational_presence, height = 11.7, width = 16.5, units = "in")  
```

## Agency Presence

```{r}
agency_by_ward <- consolidated |> 
  mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
         sector = ifelse(str_detect(sector, "Health"), "Health", sector)) |> 
  filter(sector %out% c("ETC", "Logistics") & !is.na(sector)) |> 
  filter(province != "Karnali") |>
  group_by(district, adm2_pcode, municipality, adm3_pcode, ward, sector, lead_agency, implementing_partner) |> 
  summarise(
    frequencies = sum(individuals_reached, na.rm = TRUE), 
    .groups = "drop"
  ) |> 
  filter(!is.na(ward) & ward < 20) |> 
  mutate(duplicate = ifelse(
    implementing_partner == lead_agency, 
    1, 0
  )) |> 
  mutate(implementing_partner = ifelse(
    duplicate == 1, NA_character_, implementing_partner
  )) |> 
  pivot_longer(
    lead_agency:implementing_partner, 
    names_to = "role",
    values_to = "agencies"
  ) |> 
  select(-frequencies, -duplicate) |> 
  filter(!is.na(agencies) & !is.na(municipality)) |>  
  group_by(district, adm2_pcode, municipality, adm3_pcode, ward, sector) |> 
  summarise(num_agencies = n_distinct(agencies), 
            agencies_text = paste(agencies, collapse = ",")) |> 
  left_join(
    differences |> 
      select(
        affected = affected_20260923, adm3_pcode, ward
      ), 
  by = c("adm3_pcode", "ward")
  ) |> 
  replace_na(list(affected = 0))
```

```{r}
agency_by_ward |> 
  # This is because we don't have the countrywide tables
  mutate(affected = ifelse(affected == 1, "Affected", NA_character_)) |>
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> glimpse()
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(affected), 
           ward_label,
           ""
         ))
```

```{r}
agency_by_ward |> 
select(-agencies_text) |> 
  pivot_wider(
    names_from = sector, 
    values_from = num_agencies
  ) |> 
  glimpse()
```


```{r}

food_security_presence <- agency_by_ward |> 
  select(-agencies_text) |> 
  pivot_wider(
    names_from = sector, 
    values_from = num_agencies
  ) |> 
  # This is because we don't have the countrywide tables
  mutate(affected = ifelse(affected == 1, "Affected", NA_character_)) |>
  right_join(
    wards, 
    by = c("adm3_pcode", "ward")
  )  |> 
  mutate(ward_label = as.character(ward), 
         ward_label = ifelse(
           !is.na(`Food Security`), 
           ward_label,
           ""
         )) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(aes(fill = `Protection`), colour = "grey80") +
  geom_sf(data = adm3, alpha = .25, linewidth = .75, colour = "grey70", fill = NA) +
  geom_sf_text(data = adm3 |> 
                 filter(adm2_name %in% c("Rasuwa", "Nuwakot", "Dhading", 
                                         "Chitawan", "Tanahu", "Gorkha")),
                 aes(label = adm3_name),
              alpha = .25) +
  
  scale_fill_continuous(high = "#003425", low = "#e6efd0", labels = comma, na.value = "grey99") +
    # River
  geom_sf(data = river, colour = "#0074b7", fill = "#0074b7") +
  geom_sf(aes(colour = affected), fill = NA, linewidth = .75) +
  geom_shadowtext(
      aes(label = ward_label, 
          geometry = geometry), 
      stat = "sf_coordinates", 
      size = 2.5, color = "black",  bg.color = "white", bg.r = 0.1) +
  scale_colour_manual(values = c("Affected" = "#e56a54"), 
      na.value = "grey80", 
      na.translate = FALSE) + 
  coord_sf(xlim = c(84.4, 85.6), ylim = c(27.63, 28.35)) + 
  labs(x = "", y = "", 
       fill = "Number of\nAgencies",
       colour = "Flood\nAffected", 
       title = paste0("Number of Food Security Partners by Ward"),  
       subtitle = "Ward numbers listed.") +
  theme(plot.title = element_text(size = 20, face = "bold")) +
  
  combined_logos +

  plot_layout(ncol = 1, 
              heights = c(25, 1), 
  design = "
AAAAAA
BB####
") + 
  plot_annotation(
    caption = "Sources: Nepal National Disaster Risk Reduction and Management Authority; UNOSAT; United Nations Nepal and its humanitarian partners; 5Ws 20260923."
  )

ggsave("./plots/food_security_presence.png", 
       food_security_operational_presence, 
       height = 11.7, width = 16.5, units = "in")


```

```{r}

ggsave("./plots/protection_operational_presence.png", protection_operational_presence, height = 11.7, width = 16.5, units = "in")  
```

