---
title: "Untitled"
format: html
---

```{r setup}

knitr::opts_chunk$set(echo = FALSE, fig.width=9, message = FALSE, warning=FALSE)

library(tidyverse)
library(sf)
library(readxl)
library(kableExtra)
library(flextable)
library(viridis)
library(scales)
library(janitor)

`%out%` <- Negate(`%in%`)

theme_set(theme_light())


```
# Geodata

```{r}
bagmati <- st_read("./data/shapefiles/Ward_Bagmati.shp") |> 
  st_drop_geometry()

gandaki <- st_read("./data/shapefiles/Ward_Gandaki.shp") |> 
  st_drop_geometry()


wards <- st_read("./data/shapefiles/npl_admn_ad4_py_s1_ocha_hp_wards.shp")

affected_wards <- read_xls("./data/Affected_wardsV2.xls") |> 
  janitor::clean_names()

adm3 <- st_read("./data/shapefiles/npl_admin_boundaries.shp/npl_admin3.shp")

nepal_admin <- read_xlsx("./data/npl_admin_boundaries.xlsx", 
                         sheet = 7) |> 
  select(adm3_name, adm3_pcode, adm2_name, adm2_pcode, adm1_name, adm1_pcode)

affected_municipalities_wards <- read_xls("./data/Affected_wardsv2.xls") |> 
  janitor::clean_names() |> 
  select(adm1_pcode, 
         district = adm2_en, 
         adm2_pcode,
         municipality = adm3_en, 
         adm3_pcode, 
         ward = new_ward_n) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = "adm1_pcode"
  ) |> 
  rename(province = adm1_name) |> 
  relocate(province, .before = adm1_pcode) |> 
  distinct(adm3_pcode, ward)
```



# Wards

## Functions 

```{r}
pop_proj_clean <- function(tbl) {
  tbl |> 
    setNames(c("ward", 
             "population_total", 
             "population_male", 
             "population_female", 
             "total_0_4", "male_0_4", "female_0_4", 
             "total_5_9", "male_5_9", "female_5_9",
             "total_10_14", "male_10_14", "female_10_14",
             "total_15_19", "male_15_19", "female_15_19",
             "total_20_24", "male_20_24", "female_20_24",
             "total_25_29", "male_25_29", "female_25_29",
             "total_30_34", "male_30_34", "female_30_34",
             "total_35_39", "male_35_39", "female_35_39",
             "total_40_44", "male_40_44", "female_40_44",
             "total_45_49", "male_45_49", "female_45_49",
             "total_50_54", "male_50_54", "female_50_54",
             "total_55_59", "male_55_59", "female_55_59",
             "total_60_64", "male_60_64", "female_60_64",
             "total_65_69", "male_65_69", "female_65_69",
             "total_70_74", "male_70_74", "female_70_74",
             "total_75_79", "male_75_79", "female_75_79",
             "total_80_84", "male_80_84", "female_80_84",
             "total_85_89", "male_85_89", "female_85_89",
             "total_90_94", "male_90_94", "female_90_94",
             "total_95plus", "male_95plus", "female_95plus"
             )) |> 
  filter(!is.na(ward) & !str_detect(ward, "Total")) |>
  mutate(ward = as.numeric(ward))
}

pop_proj_select <- function(tbl) {
  tbl |>
    select(province, district, municipality,
           adm1_pcode, adm2_pcode, adm3_pcode, ward,
           everything())
}
```

```{r}
nepal_admin |> 
  filter(str_detect(adm3_name, "Kamana"))
  filter(adm3_name == "Gajuri")
```

## Population projections 2026

```{r}
affected_wards_population <- read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx") |> 
  janitor::clean_names()

read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Ichchha Kamana RM-wardwise",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Chitawan", 
         municipality = "Ichchha Kamana", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0335", 
         adm3_pcode = "NP0335401") |> 
  pop_proj_select() |> 
  glimpse()
```

This is the code to bind all the ward data together from across all the individual municipal sheets. 


```{r}
proj_flat_working <- rbind(
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 3,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Rasuwa", 
         municipality = "Uttargaya", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0329", 
         adm3_pcode = "NP0329403") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 4,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Rasuwa", 
         municipality = "Gosaikunda", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0329", 
         adm3_pcode = "NP0329402") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 5,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Rasuwa", 
         municipality = "Aamachhodingmo", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0329", 
         adm3_pcode = "NP0329401") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 6,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Rasuwa", 
         municipality = "Kalika", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0329", 
         adm3_pcode = "NP0329404") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 7,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Nuwakot", 
         municipality = "Tarakeshwor", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0328", 
         adm3_pcode = "NP0328403") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 8,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Nuwakot", 
         municipality = "Kispang", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0328", 
         adm3_pcode = "NP0328402") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 9,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Nuwakot", 
         municipality = "Bidur", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0328", 
         adm3_pcode = "NP0328301") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = 10,
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Nuwakot", 
         municipality = "Belkotgadhi", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0328", 
         adm3_pcode = "NP0328302") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Galchhi RM-wardwise",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Dhading", 
         municipality = "Galchhi", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0330", 
         adm3_pcode = "NP0330410") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Gajuri RM_wardwise",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Dhading", 
         municipality = "Gajuri", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0330", 
         adm3_pcode = "NP0330409") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Benighat RerangRM_wardwise",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Dhading", 
         municipality = "Benighat Rorang", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0330", 
         adm3_pcode = "NP0330408") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Siddhalek RM",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Dhading", 
         municipality = "Siddhalek", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0330", 
         adm3_pcode = "NP0330407") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Gandaki RM",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Gandaki", 
         district = "Gorkha", 
         municipality = "Gandaki", 
         adm1_pcode = "NP04", 
         adm2_pcode = "NP0436", 
         adm3_pcode = "NP0436409") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Devghat RM-wardwise",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Gandaki", 
         district = "Tanahu", 
         municipality = "Devghat", 
         adm1_pcode = "NP04", 
         adm2_pcode = "NP0440", 
         adm3_pcode = "NP0440406") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Aanbu Khaireni RM-ward-wise",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Gandaki", 
         district = "Tanahu", 
         municipality = "Aanbu Khaireni", 
         adm1_pcode = "NP04", 
         adm2_pcode = "NP0440", 
         adm3_pcode = "NP0440405") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "SahidLakhan RM",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Gandaki", 
         district = "Gorkha", 
         municipality = "Shahid Lakhan", 
         adm1_pcode = "NP04", 
         adm2_pcode = "NP0436", 
         adm3_pcode = "NP0436408") |> 
  pop_proj_select(), 
  
  read_xlsx("./data/Copy of Affected Palikas and Wards_ward_wise_population_projection 2026 (1).xlsx", 
          sheet = "Ichchha Kamana RM-wardwise",
          skip = 2) |> 
  pop_proj_clean() |> 
  mutate(province = "Bagmati", 
         district = "Chitawan", 
         municipality = "Ichchha Kamana", 
         adm1_pcode = "NP03", 
         adm2_pcode = "NP0335", 
         adm3_pcode = "NP0335401") |> 
  pop_proj_select()
  
) |> 
   left_join(
    affected_municipalities_wards |> 
      mutate(affected = "affected"), 
    by = c("adm3_pcode", "ward")
  ) |> 
  relocate(affected, .after = ward)

proj_flat_working |> 
  rename_at(vars(population_total:female_95plus), 
            ~paste0("projection_2026_", .x)) |> 
  write_csv("./data/population_projections_2026_affected_wards_flat.csv")
```

```{r}
proj_flat_working |> 
  pivot_longer(cols = population_total:female_95plus, 
               names_to = "variable", 
               values_to = "value") |> 
  mutate(theme = "population projections 2026") |>
  mutate(disaggregation = ifelse(
    variable %in% c("population_total", "population_male", "population_female"), 
    str_remove(variable, "population_"), 
    str_extract(variable, "^[^_]+")),
    variable = case_when(
      variable == "population_male" ~ "population_overall_male", 
      variable == "population_female" ~ "population_overall_female", 
      variable == "population_total" ~ variable, 
      TRUE ~ str_replace_all(variable, "total|male|female", "age_group")
      )) |>
  relocate(theme, .after = affected) |> 
  relocate(disaggregation, .after = theme) |>
  write_csv("./data/population_projections_2026_affected_wards_long.csv")

```



## Affected wards



```{r}
proj_flat <- read_csv("./data/population_projections_2026_affected_wards_flat.csv")

proj_flat |> mutate(
  rdna_affected = case_when(
    municipality == "Bidur" & ward %in% c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 12) ~ 1, 
    municipality == "Belkotgadhi" & ward %in% c(5, 7, 8) ~ 1, 
    municipality == "Kispang" & ward == 5 ~ 1, 
    municipality == "Tarakeshwor" & ward %in% c(2, 4) ~ 1, 
    municipality == "Aamachhodingmo" & ward %in% c(1, 2, 4, 5) ~ 1, 
    municipality == "Gosaikunda" & ward %in% c(1,2, 3, 5, 6) ~ 1, 
    municipality == "Uttargaya" & ward %in% c(1, 2, 3, 4, 5) ~ 1, 
    municipality == "Kalika" & ward == 1 ~ 1, 
    municipality == "Siddhalek" & ward %in% c(3,4, 6, 7) ~ 1, 
    municipality == "Benighat Rorang" & ward %in% c(3, 5, 7, 8, 9, 10) ~ 1, 
    municipality == "Gajuri" & ward %in% c(1, 2, 5, 6) ~ 1, 
    municipality == "Galchhi" & ward %in% c(1, 2, 4, 6, 8) ~ 1, 
    municipality == "Ichchha Kamana" & ward %in% c(3,4, 5, 6) ~ 1, 
    municipality == "Shahid Lakhan" & ward %in% c(3,4) ~ 1, 
    municipality == "Gandaki" & ward %in% c(1, 2, 6, 7, 8) ~ 1, 
    TRUE ~ NA_real_ 
  )) |>
  mutate(
  flash_appeal_affected = case_when(
    municipality == "Bidur" & ward %in% c(1, 4, 5, 9, 10) ~ 1, 
    municipality == "Belkotgadhi" & ward %in% c(5, 7, 8) ~ 1, 
    municipality == "Kispang" & ward == 5 ~ 1, 
    municipality == "Tarakeshwor" & ward %in% c(2, 4) ~ 1, 
    municipality == "Aamachhodingmo" & ward %in% c(1) ~ 1, 
    municipality == "Gosaikunda" & ward %in% c(1,2, 3, 5) ~ 1, 
    municipality == "Uttargaya" & ward %in% c(1, 2, 3, 4, 5) ~ 1, 
    municipality == "Kalika" & ward == 1 ~ 1, 
    municipality == "Siddhalek" & ward %in% c(3,4, 6, 7) ~ 1, 
    municipality == "Benighat Rorang" & ward %in% c(3, 5, 7, 9,10) ~ 1, 
    municipality == "Gajuri" & ward %in% c(1, 2, 5, 6) ~ 1, 
    municipality == "Galchhi" & ward %in% c(1, 2,4, 6, 8) ~ 1, 
    municipality == "Ichchha Kamana" & ward %in% c(3,4) ~ 1, 
    municipality == "Shahid Lakhan" & ward %in% c(2, 3, 5, 6) ~ 1, 
    municipality == "Gandaki" & ward %in% c(1, 2, 6, 7, 8) ~ 1, 
    municipality == "Devghat" & ward %in% c(4, 5) ~ 1, 
    municipality == "Aanbu Khaireni" & ward %in% c(4, 5) ~ 1, 
    TRUE ~ NA_real_ 
  )) |>
  select(-affected) |> 
  select(district, adm2_pcode, municipality, adm3_pcode, ward,
         projection_2026_population_total,
         flash_appeal_affected, rdna_affected) |> 
  mutate(different = case_when(
    flash_appeal_affected == rdna_affected ~ 0, 
    is.na(flash_appeal_affected) & is.na(rdna_affected) ~ 0, 
    TRUE ~ 1
  )) |> 
  filter(!is.na(flash_appeal_affected) | !is.na(rdna_affected)) |> 
  replace_na(list(flash_appeal_affected = 0, 
                  rdna_affected = 0)) |> 
  mutate(ndrrma_new = case_when(
    municipality == "Gajuri" & ward == 1 ~ 0, 
    municipality == "Siddhalek" & ward %in% c(3, 4) ~ 0, 
    municipality == "Ichchha Kamana" & ward == 6 ~ 0, 
    municipality == "Kalika" &  ward == 5 ~ 0, 
    municipality == "Kispang" & ward == 3 ~ 0, 
    municipality == "Gosaikunda" & ward == 6 ~ 0, 
    municipality == "Aamachhodingmo" & ward %in% c(2, 4) ~ 0,
    TRUE ~ rdna_affected
  )) |> 
  
  write_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv")


  summarise(population_wards_flash_appeal_affected = sum(projection_2026_population_total[flash_appeal_affected == 1]),
            population_wards_rdna_affected = sum(projection_2026_population_total[rdna_affected == 1]))
  
  
  write_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv")
```


```{r}
read_csv("./data/FILTERED_nepal_census2021_ward_level_household_tables_bagmati_gandaki_flat.csv") |> 
  glimpse()
```


```{r}
proj_flat_working |> glimpse()
```


```{r}
affected_wards <- read_xls("./data/Affected_wardsv2.xls") |> 
  janitor::clean_names() |> 
  select(adm1_pcode, 
         district = adm2_en, 
         adm2_pcode,
         municipality = adm3_en, 
         adm3_pcode, 
         ward = new_ward_n) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = "adm1_pcode"
  ) |> 
  rename(province = adm1_name) |> 
  relocate(province, .before = adm1_pcode) |>
  mutate(affected = "affected")

  write_csv("./data/affected_ward_simple_20260910.csv")
  glimpse()
```

## Settlements

```{r}
settlements <- st_read("./data/shapefiles/npl_stle_stl_pt_s0_osm_pp_settlements.shp") |> 
  glimpse()

settlements |> 
  st_drop_geometry() |> 
  count(fclass)
```

## Impacted buildings

```{r}
impacted_buildings <- read_xlsx("./data/impacted_buildings.xlsx") |> 
  mutate(municipality = ifelse(municipality == "Ichcha Kamana", 
                               "Ichchha Kamana", 
                               municipality)) |> 
  left_join(
    nepal_admin |> 
      distinct(adm3_name, adm1_pcode, adm2_pcode, adm3_pcode), 
    by = c("municipality" = "adm3_name")
  ) |> 
  filter(adm3_pcode != "NP0327301" & adm3_pcode != "NP0335301")
```


# Census

## Functions


```{r}

# Two versions, depends on the structure of the excel file
ward_fill_filter <- function(tbl) {
  tbl |> 
    fill(province, .direction = "down") |>
    fill(district, .direction = "down") |>
    fill(municipality, .direction = "down") |>
    filter(!is.na(ward))
}

ward_fill_filter2 <- function(tbl) {
  tbl |> 
    fill(province, .direction = "down") |>
    fill(district, .direction = "down") |>
    fill(municipality, .direction = "down") |>
    fill(ward, .direction = "down") |> 
    filter(!is.na(ward))
}

# District name cleaning
bagmati_district_names <- function(tbl) {
  tbl |>
    mutate(province = "Bagmati") |> 
    mutate(district = as.character(district)) |>
    mutate(
      district = case_when(
        district == 23 ~ "Dolakha",
        district == 24 ~ "Sindhupalchok",
        district == 25 ~ "Rasuwa",
        district == 26 ~ "Dhading",
        district == 27 ~ "Nuwakot",
        district == 28 ~ "Kathmandu",
        district == 29 ~ "Bhaktapur",
        district == 30 ~ "Lalitpur",
        district == 31 ~ "Kavrepalanchok",
        district == 32 ~ "Ramechhap",
        district == 33 ~ "Sindhuli",
        district == 34 ~ "Makwanpur",
        district == 35 ~ "Chitawan",
        TRUE ~ district
      )
    ) |> 
    filter(name %out% c("Dolakha", "Sindhupalchok", "Rasuwa", "Dhading", 
                      "Nuwakot", "Kathmandu", "Bhaktapur", "Lalitpur",
                      "Kavrepalanchok", "Ramechhap", "Sindhuli", "Makwanpur", 
                      "Chitawan", "NEPAL", "BAGMATI")) |> 
  select(-municipality) |> 
  rename(municipality = name) |> 
  mutate(ward = ifelse(ward == "Total", "All Wards", ward))
}

gandaki_district_names <- function(tbl) {
  tbl |>
    mutate(province = "Gandaki") |>
    mutate(district = as.character(district)) |>
    mutate(
      district = case_when(
        district == 36 ~ "Gorkha",
        district == 37 ~ "Manang",
        district == 38 ~ "Mustang",
        district == 39 ~ "Myagdi",
        district == 40 ~ "Kaski",
        district == 41 ~ "Lamjung",
        district == 42 ~ "Tanahu",
        district == 43 ~ "Nawalparasi East",
        district == 44 ~ "Syangja",
        district == 45 ~ "Parbat",
        district == 46 ~ "Baglung",
        TRUE ~ district
      )
    ) |> 
    filter(name %out% c("Gorkha", "Manang", "Mustang", "Myagdi", "Kaski",
                      "Lamjung", "Tanahu", "Nawalparasi East", "Syangja", "Parbat",
                      "Baglung", "NEPAL", "GANDAKI")) |> 
  select(-municipality) |> 
  rename(municipality = name) |> 
  mutate(ward = ifelse(ward == "Total", "All Wards", ward))
}
```

## Households 

### Bagmati 

```{r bagmati warning=FALSE, message=FALSE}
bagmati <- cbind(
  read_xlsx("./data/census/WRD_Bagmati_Hhld01-OwnershipOfHouse.xlsx", 
          skip = 3) |>
  setNames(c("province", "district", "municipality", "ward", "ownership_total", 
             "ownership_owned", 
             "ownership_rented", 
             "ownership_institutional", 
             "ownership_other")) |> 
  ward_fill_filter(), 
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld02-FoundationOfHouse.xlsx", 
          skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "foundation_total", 
             "foundation_mud", 
             "foundation_mud_bonded_bricks_stone", 
             "foundation_cement_bonded_bricks_stone", 
             "foundation_reinforced_cement_concrete_with_pillars", 
             "foundation_wooden_pillars", 
             "foundation_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld03-OuterWallOfHouse.xlsx", 
          skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "outer_wall_total",
             "outer_wall_mud_bonded_bricks_stone", 
             "outer_wall_cement_bonded_bricks_stone", 
             "outer_wall_wood_planks", 
             "outer_wall_bamboo", 
             "outer_wall_unbaked_bricks", 
             "outer_wall_galvanised_sheet", 
             "outer_wall_prefabricated_sheet", 
             "outer_wall_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld04-RoofOfHouse.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "roof_total",
             "roof_galvanised_sheet", 
             "roof_reinforced_cement_concrete", 
             "roof_thatch_straw", 
             "roof_tile", 
             "roof_stone_slate", 
             "roof_wood_planks", 
             "roof_mud", 
             "roof_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld05-FloorOfHouse.xlsx", 
          skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "floor_total",
             "floor_mud", 
             "floor_wooden_plank_bamboo", 
             "floor_bricks_stone", 
             "floor_ceramic_tile", 
             "floor_cemented", 
             "floor_other")) |>
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld06-SourceOfDrinkingWater.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "drinking_water_total",
           "drinking_water_tap_piped_within_premises", 
           "drinking_water_tap_piped_outside_premises", 
           "drinking_water_tubewell_handpump", 
           "drinking_water_covered_well_kuwa", 
           "drinking_water_uncovered_well_kuwa", 
           "drinking_water_spout_water", 
           "drinking_water_river_stream", 
           "drinking_water_jar_bottle", 
           "drinking_water_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld07-CookingFuel.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "cooking_fuel_total",
             "cooking_fuel_wood_firewood", 
             "cooking_fuel_lpg", 
             "cooking_fuel_electricity", 
             "cooking_fuel_cowdung", 
             "cooking_fuel_biogas", 
             "cooking_fuel_kerosene", 
             "cooking_fuel_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward),
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld08-LightingFuel.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "lighting_fuel_total",
             "lighting_electricity", 
             "lighting_solar", 
             "lighting_kerosene", 
             "lighting_biogas", 
             "lighting_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward),
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld09-ToiletFacility.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "toilet_total",
             "toilet_flush_public_sewerage", 
             "toilet_flush_septic_tank", 
             "toilet_pit", 
             "toilet_public", 
             "toilet_no_toilet")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward),
  
  read_xlsx("./data/census/WRD_Bagmati_Hhld10-HouseholdAmenities.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "hh_amenities_total",
             "hh_amenities_without", 
             "hh_amenities_at_least_one", 
             "hh_amenities_radio", 
             "hh_amenities_television", 
             "hh_amenities_landline", 
             "hh_amenities_mobile_phone_ordinary", 
             "hh_amenities_mobile_phone_smart", 
             "hh_amenities_computer_laptop", 
             "hh_amenities_internet",
             "hh_amenities_car_jeep_van", 
             "hh_amenities_motorcycle_scooter", 
             "hh_amenities_bicycle", 
             "hh_amenities_electric_fan", 
             "hh_amenities_refridgerator", 
             "hh_amenities_washing_machine", 
             "hh_amenities_air_conditioner")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward),
  
  read_xlsx("./data/census/Rev_Bagmati_Hhld_WealthQuintileHousehold_Ward_formated.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward", "wealth_quintile_total",
             "wealth_quintile_poorest_quintile_count", 
             "wealth_quintile_poorer_quintile_count", 
             "wealth_quintile_middle_quintile_count", 
             "wealth_quintile_richer_quintile_count", 
             "wealth_quintile_richest_quintile_count", 
             "wealth_quintile_poorest_quintile_pc", 
             "wealth_quintile_poorer_quintile_pc",
             "wealth_quintile_middle_quintile_pc", 
             "wealth_quintile_richer_quintile_pc", 
             "wealth_quintile_richest_quintile_pc")) |> 
  bagmati_district_names() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/Rev_Bagmati_Hhld_QualityOfHouse_Ward_formated.xlsx", skip = 2) |> 
   setNames(c("province", "district", "municipality", "name", "ward", "house_quality_total",
             "house_quality_most_adequate_count", 
             "house_quality_adequate_count", 
             "house_quality_moderate_count", 
             "house_quality_inadequate_count", 
             "house_quality_least_adequate_count", 
             "house_quality_most_adequate_pc", 
             "house_quality_adequate_pc",
             "house_quality_moderate_pc", 
             "house_quality_inadequate_pc", 
             "house_quality_least_adequate_pc")) |> 
 bagmati_district_names() |>  
 select(-province, -district, -municipality, -ward) 
)
```

### Gandaki

```{r}
gandaki <- cbind(
  read_xlsx("./data/census/WRD_Gandaki_Hhld01-OwnershipOfHouse.xlsx", 
          skip = 3) |>
  setNames(c("province", "district", "municipality", "ward", "ownership_total", 
             "ownership_owned", 
             "ownership_rented", 
             "ownership_institutional", 
             "ownership_other")) |> 
  ward_fill_filter(), 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld02-FoundationOfHouse.xlsx", 
          skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "foundation_total", 
             "foundation_mud", 
             "foundation_mud_bonded_bricks_stone", 
             "foundation_cement_bonded_bricks_stone", 
             "foundation_reinforced_cement_concrete_with_pillars", 
             "foundation_wooden_pillars", 
             "foundation_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward) , 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld03-OuterWallOfHouse.xlsx", 
          skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "outer_wall_total",
             "outer_wall_mud_bonded_bricks_stone", 
             "outer_wall_cement_bonded_bricks_stone", 
             "outer_wall_wood_planks", 
             "outer_wall_bamboo", 
             "outer_wall_unbaked_bricks", 
             "outer_wall_galvanised_sheet", 
             "outer_wall_prefabricated_sheet", 
             "outer_wall_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld04-RoofOfHouse.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "roof_total",
             "roof_galvanised_sheet", 
             "roof_reinforced_cement_concrete", 
             "roof_thatch_straw", 
             "roof_tile", 
             "roof_stone_slate", 
             "roof_wood_planks", 
             "roof_mud", 
             "roof_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld05-FloorOfHouse.xlsx", 
          skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "floor_total",
             "floor_mud", 
             "floor_wooden_plank_bamboo", 
             "floor_bricks_stone", 
             "floor_ceramic_tile", 
             "floor_cemented", 
             "floor_other")) |>
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward) , 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld06-SourceOfDrinkingWater.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "drinking_water_total",
           "drinking_water_tap_piped_within_premises", 
           "drinking_water_tap_piped_outside_premises", 
           "drinking_water_tubewell_handpump", 
           "drinking_water_covered_well_kuwa", 
           "drinking_water_uncovered_well_kuwa", 
           "drinking_water_spout_water", 
           "drinking_water_river_stream", 
           "drinking_water_jar_bottle", 
           "drinking_water_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward) , 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld07-CookingFuel.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "cooking_fuel_total",
             "cooking_fuel_wood_firewood", 
             "cooking_fuel_lpg", 
             "cooking_fuel_electricity", 
             "cooking_fuel_cowdung", 
             "cooking_fuel_biogas", 
             "cooking_fuel_kerosene", 
             "cooking_fuel_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld08-LightingFuel.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "lighting_fuel_total",
             "lighting_electricity", 
             "lighting_solar", 
             "lighting_kerosene", 
             "lighting_biogas", 
             "lighting_other")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld09-ToiletFacility.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "toilet_total",
             "toilet_flush_public_sewerage", 
             "toilet_flush_septic_tank", 
             "toilet_pit", 
             "toilet_public", 
             "toilet_no_toilet")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/WRD_Gandaki_Hhld10-HouseholdAmenities.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "hh_amenities_total",
             "hh_amenities_without", 
             "hh_amenities_at_least_one", 
             "hh_amenities_radio", 
             "hh_amenities_television", 
             "hh_amenities_landline", 
             "hh_amenities_mobile_phone_ordinary", 
             "hh_amenities_mobile_phone_smart", 
             "hh_amenities_computer_laptop", 
             "hh_amenities_internet",
             "hh_amenities_car_jeep_van", 
             "hh_amenities_motorcycle_scooter", 
             "hh_amenities_bicycle", 
             "hh_amenities_electric_fan", 
             "hh_amenities_refridgerator", 
             "hh_amenities_washing_machine", 
             "hh_amenities_air_conditioner")) |> 
  ward_fill_filter() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/Rev_Gandaki_Hhld_WealthQuintileHousehold_Ward_formated.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward", "wealth_quintile_total",
             "wealth_quintile_poorest_quintile_count", 
             "wealth_quintile_poorer_quintile_count", 
             "wealth_quintile_middle_quintile_count", 
             "wealth_quintile_richer_quintile_count", 
             "wealth_quintile_richest_quintile_count", 
             "wealth_quintile_poorest_quintile_pc", 
             "wealth_quintile_poorer_quintile_pc",
             "wealth_quintile_middle_quintile_pc", 
             "wealth_quintile_richer_quintile_pc", 
             "wealth_quintile_richest_quintile_pc")) |> 
  gandaki_district_names() |> 
  # One extra municipality (electoral constituency, really)
  # That does not appear in the other datasets
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/Rev_Gandaki_Hhld_QualityOfHouse_Ward_formated.xlsx", skip = 2) |> 
   setNames(c("province", "district", "municipality", "name", "ward", "house_quality_total",
             "house_quality_most_adequate_count", 
             "house_quality_adequate_count", 
             "house_quality_moderate_count", 
             "house_quality_inadequate_count", 
             "house_quality_least_adequate_count", 
             "house_quality_most_adequate_pc", 
             "house_quality_adequate_pc",
             "house_quality_moderate_pc", 
             "house_quality_inadequate_pc", 
             "house_quality_least_adequate_pc")) |> 
  gandaki_district_names() |> 
  # One extra municipality (electoral constituency, really)
  # That does not appear in the other datasets
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward)
  
  
  ) 
  
```



### Combined

```{r census-combined-check}
bagmati |> 
  select(province, district, municipality, ward, contains("total")) |> 
  mutate(difference = ownership_total - foundation_total + 
           outer_wall_total - roof_total +
           floor_total - drinking_water_total +
           cooking_fuel_total - lighting_fuel_total + 
           toilet_total - hh_amenities_total + 
           wealth_quintile_total - house_quality_total) |> 
  filter(difference != 0)


gandaki |> 
  select(province, district, municipality, ward, contains("total")) |> 
  mutate(difference = ownership_total - foundation_total + 
           outer_wall_total - roof_total +
           floor_total - drinking_water_total +
           cooking_fuel_total - lighting_fuel_total + 
           toilet_total - hh_amenities_total + 
           wealth_quintile_total - house_quality_total) |> 
  filter(difference != 0)
  
```


```{r}
# Combining and cleaning place names to match the pcode dataset 
bagmati_gandaki_hhd <- rbind(
  bagmati, gandaki
) |> 
  mutate(district = ifelse(district == "Nawalparasi (East)", "Nawalparasi East", district)) |>
  mutate(municipality = str_remove_all(municipality, "Gaunpalika|Municipality"), 
         municipality = str_trim(municipality)) |> 
  mutate(municipality = case_when(
    municipality == "Melanchi" ~ "Melamchi", 
    municipality == "Kathmandu Metropolitian City" ~ "Kathmandu", 
    municipality == "Lalitpur Metropolitian City" ~ "Lalitpur", 
    municipality == "Hetauda Sub-Metropolitian City" ~ "Hetauda", 
    municipality == "Bharatpur Metropolitian City" ~ "Bharatpur", 
    municipality == "Manang Ngisyang" ~ "Ngisyang", 
    municipality == "Pokhara Metropolitian City" ~ "Pokhara", 
    TRUE ~ municipality
  )) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  ) |> 
  rename(total_households = ownership_total) |> 
  select(-foundation_total, -outer_wall_total, -roof_total, -floor_total, 
         -drinking_water_total, -cooking_fuel_total, -lighting_fuel_total, 
         -toilet_total, -hh_amenities_total, -wealth_quintile_total, 
         -house_quality_total) |> 
  rename_at(vars(ownership_owned:ownership_other), 
            ~str_replace(.x, "ownership", "home_ownership")) |> 
  left_join(
     read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv") |> 
  select(adm2_pcode, adm3_pcode, ward, rdna_affected) |> 
  mutate(rdna_affected = ifelse(rdna_affected == 0, NA_real_, rdna_affected), 
         ward = as.character(ward)), 
  by = c("adm2_pcode", "adm3_pcode", "ward")
  ) |> 
  relocate(rdna_affected, .after = ward)
```

## Population

### Bagmati

```{r}
bagmati_individual <- cbind(
  # households and population
  read_xlsx("./data/census/WRD_Bagmati_Indv01-HouseholdAndPopulation.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "total_households",
             "population_total", 
             "population_male",
             "population_female",
             "average_household_size", 
             "sex_ratio")) |> 
  ward_fill_filter(),
  # select(-province, -district, -municipality, -ward), 
  
  # Economic activity
  read_xlsx("./data/census/WRD_Bagmati_Indv05-EconomicActivity.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "sex",
             "population_10_years_and_older",
             "usually_economically_active_employed",
             "usually_economically_active_unemployed", 
             "not_usually_economically_active", 
             "not_economically_active", 
             "economic_activity_not_stated")) |> 
  ward_fill_filter2() |> 
  filter(!is.na(sex)) |> 
  mutate(sex = str_to_lower(sex)) |> 
  pivot_wider(
    names_from = c("sex"), 
    values_from = c("population_10_years_and_older",
                    "usually_economically_active_employed",
                    "usually_economically_active_unemployed", 
                    "not_usually_economically_active", 
                    "not_economically_active", 
                    "economic_activity_not_stated"), 
    names_glue ="{sex}_{.value}"
  )  |> 
    select(-province, -district, -municipality, -ward),
  
  # Five-year age group
  read_xlsx("./data/census/WRD_Bagmati_Indv02-FiveYearsAgeGroupsAndSex.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", 
             "five_year_age_group", 
             "total",
             "male", 
             "female")) |> 
  ward_fill_filter2() |> 
  filter(!is.na(five_year_age_group)) |> 
  mutate(five_year_age_group = str_replace(five_year_age_group, "-| ", "_"), 
         five_year_age_group = str_to_lower(five_year_age_group),
         five_year_age_group = str_replace(five_year_age_group, " yrs.", "_yrs"), 
         five_year_age_group = str_remove(five_year_age_group, "\\."), 
         five_year_age_group = str_replace(five_year_age_group, "\\+", "plus")) |> 
  pivot_wider(
    names_from = "five_year_age_group", 
    values_from = c("total", "male", "female"), 
    names_glue = "{.value}_{five_year_age_group}"
  ) |> 
  select(-province, -district, -municipality, -ward),
  
  # Educational status children
  read_xlsx("./data/census/Indv_Bagmati_educationaStatusChild_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
      "total_children_5_17", 
      "male_children_5_17", 
      "female_children_5_17", 
      "currently_attending_school_male", 
      "currently_attending_school_female", 
      "oos_ever_attended_school_male", 
      "oos_ever_attended_school_female", 
      "oos_never_attended_school_male", 
      "oos_never_attended_school_female", 
      "currently_attending_school_total_pc", 
      "currently_attending_school_male_pc", 
      "currently_attending_school_female_pc", 
      "oos_ever_attended_school_total_pc", 
      "oos_ever_attended_school_male_pc", 
      "oos_ever_attended_school_female_pc", 
      "oos_never_attended_school_total_pc", 
      "oos_never_attended_school_male_pc", 
      "oos_never_attended_school_female_pc")
  ) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |>
  select(-province, -district, -municipality, -ward),
  
  # Adult literacy
  read_xlsx("./data/census/Indv_Bagmati_Adultliteracy15plus_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
      "population_15plus_total",
      "population_15plus_male", 
      "population_15plus_female", 
      "literate_population_total", 
      "literate_population_male", 
      "literate_population_female", 
      "literacy_rate_total", 
      "literacy_rate_male", 
      "literacy_rate_female"
      )
  ) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |>
  select(-province, -district, -municipality, -ward),
  
  # Dependency ratios
  read_xlsx("./data/census/Indv_Bagmati_BroadAge_dependency_ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_0_14", 
             "population_15_64", 
             "population_65plus", 
             "total_population", 
             "child_dependency_ratio", 
             "elderly_dependency_ratio",  
             "total_dependency_ratio")) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  select(-province, -district, -municipality, -ward) |> 
  select(-total_population),
  
  # Education level
  read_xlsx("./data/census/Indv_Bagmati_educationalLevel_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_5plus_total", 
             "population_5plus_male", 
             "population_5plus_female", 
             "education_level_illiterate_male", 
             "education_level_illiterate_female", 
             "education_level_early_childhood_male", 
             "education_level_early_childhood_female", 
             "education_level_basic_level_male", 
             "education_level_basic_level_female", 
             "education_level_secondary_male", 
             "education_level_secondary_female", 
             "education_level_higher_education_male", 
             "education_level_higher_education_female", 
             "education_level_other_male", 
             "education_level_other_female", 
             "education_level_illiterate_pc_total", 
             "education_level_illiterate_pc_male", 
             "education_level_illiterate_pc_female", 
             "education_level_early_childhood_pc_total", 
             "education_level_early_childhood_pc_male", 
             "education_level_early_childhood_pc_female", 
             "education_level_basic_level_pc_total", 
             "education_level_basic_level_pc_male", 
             "education_level_basic_level_pc_female", 
             "education_level_secondary_pc_total", 
             "education_level_secondary_pc_male", 
             "education_level_secondary_pc_female", 
             "education_level_higher_education_pc_total",
             "education_level_higher_education_pc_male", 
             "education_level_higher_education_pc_female", 
             "education_level_other_pc_total", 
             "education_level_other_pc_male", 
             "education_level_other_pc_female"
             )) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  select(-province, -district, -municipality, -ward), 
  
  # Urbanisation
  read_xlsx("./data/census/Indv_Bagmati_DegreeOfUrbanization_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_total", 
             "population_male", 
             "population_female",
             "population_urban", 
             "population_peri_urban",
             "population_rural", 
             "population_pc_urban", 
             "population_pc_peri_urban", 
             "population_pc_rural")) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  select(-province, -district, -municipality, -ward, 
         -population_total, -population_male, -population_female),
  
  # Child marriage
  read_xlsx("./data/census/Indv_Bagmati_ChildmariageBefore18_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_20_24_total", 
             "population_20_24_male", 
             "population_20_24_female", 
             "population_married_before_18_total", 
             "population_married_before_18_male", 
             "population_married_before_18_female", 
             "child_marriage_rate_total", 
             "child_marriage_rate_male", 
             "child_marriage_rate_female")) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/Indv_Bagmati_disability_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "total_population", 
             "population_with_disabilities", 
             "population_without_disabilities", 
             "population_disability_not_reported", 
             "disability_prevlance_rate")) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  select(-province, -district, -municipality, -ward), 

read_xlsx("./data/census/Indv_Bagmati_EmpAgriAndNonAgriculture_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
    "employed_population_total", 
    "employed_population_male", 
    "employed_population_female", 
    "agricultural_employment_total", 
    "agricultural_employment_male", 
    "agricultural_employment_female", 
    "non_agricultural_employment_total", 
    "non_agriculrual_employment_male", 
    "non_agricultural_employment_female", 
    "agricultural_employment_pc_total", 
    "agricultural_employment_pc_male", 
    "agricultural_employment_pc_female", 
    "non_agricultural_employment_pc_total", 
    "non_agriculrual_employment_pc_male", 
    "non_agricultural_employment_pc_female")
  ) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  select(-province, -district, -municipality, -ward)
)
```


### Gandaki

```{r}
gandaki_individual <- cbind(
  # households and population
  read_xlsx("./data/census/WRD_Gandaki_Indv01-HouseholdAndPopulation.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "total_households",
             "population_total", 
             "population_male",
             "population_female",
             "average_household_size", 
             "sex_ratio")) |> 
  ward_fill_filter() |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)"),
  # select(-province, -district, -municipality, -ward), 
  
  # Economic activity
  read_xlsx("./data/census/WRD_Gandaki_Indv05-EconomicActivity.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "sex",
             "population_10_years_and_older",
             "usually_economically_active_employed",
             "usually_economically_active_unemployed", 
             "not_usually_economically_active", 
             "not_economically_active", 
             "economic_activity_not_stated")) |> 
  ward_fill_filter2() |> 
  filter(!is.na(sex)) |> 
  mutate(sex = str_to_lower(sex)) |> 
  pivot_wider(
    names_from = c("sex"), 
    values_from = c("population_10_years_and_older",
                    "usually_economically_active_employed",
                    "usually_economically_active_unemployed", 
                    "not_usually_economically_active", 
                    "not_economically_active", 
                    "economic_activity_not_stated"), 
    names_glue ="{sex}_{.value}"
  )  |> 
    filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
    select(-province, -district, -municipality, -ward),
  
  # Five-year age group
  read_xlsx("./data/census/WRD_Gandaki_Indv02-FiveYearsAgeGroupsAndSex.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", 
             "five_year_age_group", 
             "total",
             "male", 
             "female")) |> 
  ward_fill_filter2() |> 
  filter(!is.na(five_year_age_group)) |> 
  mutate(five_year_age_group = str_replace(five_year_age_group, "-| ", "_"), 
         five_year_age_group = str_to_lower(five_year_age_group),
         five_year_age_group = str_replace(five_year_age_group, " yrs.", "_yrs"), 
         five_year_age_group = str_remove(five_year_age_group, "\\."), 
         five_year_age_group = str_replace(five_year_age_group, "\\+", "plus")) |> 
  pivot_wider(
    names_from = "five_year_age_group", 
    values_from = c("total", "male", "female"), 
    names_glue = "{.value}_{five_year_age_group}"
  ) |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward),
  
  # Educational status children
  # Missing one ward
  read_xlsx("./data/census/Indv_Gandaki_educationaStatusChild_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
      "total_children_5_17", 
      "male_children_5_17", 
      "female_children_5_17", 
      "currently_attending_school_male", 
      "currently_attending_school_female", 
      "oos_ever_attended_school_male", 
      "oos_ever_attended_school_female", 
      "oos_never_attended_school_male", 
      "oos_never_attended_school_female", 
      "currently_attending_school_total_pc", 
      "currently_attending_school_male_pc", 
      "currently_attending_school_female_pc", 
      "oos_ever_attended_school_total_pc", 
      "oos_ever_attended_school_male_pc", 
      "oos_ever_attended_school_female_pc", 
      "oos_never_attended_school_total_pc", 
      "oos_never_attended_school_male_pc", 
      "oos_never_attended_school_female_pc")
  ) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |>
  add_row(
    province = "Gandaki", 
    district = "Mustang", 
    municipality = "Lo Ghekar Damodarkunda Gaunpalika", 
    ward = "5", 
    .after = 142) |>
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward),
  
  # Adult literacy
  read_xlsx("./data/census/Indv_Gandaki_Adultliteracy15plus_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
      "population_15plus_total",
      "population_15plus_male", 
      "population_15plus_female", 
      "literate_population_total", 
      "literate_population_male", 
      "literate_population_female", 
      "literacy_rate_total", 
      "literacy_rate_male", 
      "literacy_rate_female"
      )
  ) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |>
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward),
  
  # Dependency ratios
  read_xlsx("./data/census/Indv_Gandaki_BroadAge_dependency_ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_0_14", 
             "population_15_64", 
             "population_65plus", 
             "total_population", 
             "child_dependency_ratio", 
             "elderly_dependency_ratio",  
             "total_dependency_ratio")) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward) |> 
  select(-total_population),
  
  # Education level
  read_xlsx("./data/census/Indv_Gandaki_educationalLevel_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_5plus_total", 
             "population_5plus_male", 
             "population_5plus_female", 
             "education_level_illiterate_male", 
             "education_level_illiterate_female", 
             "education_level_early_childhood_male", 
             "education_level_early_childhood_female", 
             "education_level_basic_level_male", 
             "education_level_basic_level_female", 
             "education_level_secondary_male", 
             "education_level_secondary_female", 
             "education_level_higher_education_male", 
             "education_level_higher_education_female", 
             "education_level_other_male", 
             "education_level_other_female", 
             "education_level_illiterate_pc_total", 
             "education_level_illiterate_pc_male", 
             "education_level_illiterate_pc_female", 
             "education_level_early_childhood_pc_total", 
             "education_level_early_childhood_pc_male", 
             "education_level_early_childhood_pc_female", 
             "education_level_basic_level_pc_total", 
             "education_level_basic_level_pc_male", 
             "education_level_basic_level_pc_female", 
             "education_level_secondary_pc_total", 
             "education_level_secondary_pc_male", 
             "education_level_secondary_pc_female", 
             "education_level_higher_education_pc_total",
             "education_level_higher_education_pc_male", 
             "education_level_higher_education_pc_female", 
             "education_level_other_pc_total", 
             "education_level_other_pc_male", 
             "education_level_other_pc_female"
             )) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward), 
  
  # Urbanisation
  read_xlsx("./data/census/Indv_Gandaki_DegreeOfUrbanization_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_total", 
             "population_male", 
             "population_female",
             "population_urban", 
             "population_peri_urban",
             "population_rural", 
             "population_pc_urban", 
             "population_pc_peri_urban", 
             "population_pc_rural")) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward, 
         -population_total, -population_male, -population_female),
  
  # Child marriage
  read_xlsx("./data/census/Indv_Gandaki_ChildmariageBefore18_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_20_24_total", 
             "population_20_24_male", 
             "population_20_24_female", 
             "population_married_before_18_total", 
             "population_married_before_18_male", 
             "population_married_before_18_female", 
             "child_marriage_rate_total", 
             "child_marriage_rate_male", 
             "child_marriage_rate_female")) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/Indv_Gandaki_disability_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "total_population", 
             "population_with_disabilities", 
             "population_without_disabilities", 
             "population_disability_not_reported", 
             "disability_prevlance_rate")) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward), 
  
  read_xlsx("./data/census/Indv_Gandaki_EmpAgriAndNonAgriculture_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
    "employed_population_total", 
    "employed_population_male", 
    "employed_population_female", 
    "agricultural_employment_total", 
    "agricultural_employment_male", 
    "agricultural_employment_female", 
    "non_agricultural_employment_total", 
    "non_agriculrual_employment_male", 
    "non_agricultural_employment_female", 
    "agricultural_employment_pc_total", 
    "agricultural_employment_pc_male", 
    "agricultural_employment_pc_female", 
    "non_agricultural_employment_pc_total", 
    "non_agriculrual_employment_pc_male", 
    "non_agricultural_employment_pc_female")
  ) |> 
  ward_fill_filter() |> 
  gandaki_district_names() |> 
  filter(municipality != "Nawalparasi (Bardaghat Susta East)") |> 
  select(-province, -district, -municipality, -ward)
) 
```




### Combined Individual 


#### Join population density as second-last step 

```{r}
population_densities <- rbind(read_xlsx("./data/census/Bagmati_Ward level density.xlsx", skip = 2) |> 
  setNames(c("province_code", "municipality_code", "ward_code", 
           "province", "district", "municipality", "ward",
           "population_2011", 
           "total_population", 
           "population_male", 
           "population_female", 
           "population_density")) |> 
  mutate(municipality = str_remove_all(municipality, "Gaunpalika|Municipality"),
         district = str_to_title(district),
         municipality = str_trim(municipality)) |> 
  mutate(municipality = case_when(
    municipality == "Melanchi" ~ "Melamchi", 
    str_detect(municipality, "Kathmandu Metropolitian City|KathmanduMetropolitian City") ~ "Kathmandu", 
    str_detect(municipality, "Lalitpur Metropolitian City|LalitpurMetropolitian City") ~ "Lalitpur",
    str_detect(municipality, "Hetauda Sub-Metropolitian City|HetaudaSub-Metropolitian City") ~ "Hetauda",
    str_detect(municipality, "Bharatpur Metropolitian City|BharatpurMetropolitian City") ~ "Bharatpur",
    municipality == "Manang Ngisyang" ~ "Ngisyang", 
    municipality == "Pokhara Metropolitian City" ~ "Pokhara", 
    TRUE ~ municipality
  )) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  ) |> 
  select(adm3_pcode, ward, population_density),

  read_xlsx("./data/census/Gandaki_Ward level density.xlsx", skip = 2) |> 
  setNames(c("province_code", "municipality_code", "ward_code", 
           "province", "district", "municipality", "ward",
           "population_2011", 
           "total_population", 
           "population_male", 
           "population_female", 
           "population_density")) |> 
  mutate(municipality = str_remove_all(municipality, "Gaunpalika|Municipality"),
         district = str_to_title(district),
         municipality = str_trim(municipality), 
         district = ifelse(district == "Nawalparasi (East)", 
                           "Nawalparasi East", 
                           district)) |> 
  mutate(municipality = case_when(
    municipality == "Melanchi" ~ "Melamchi", 
    str_detect(municipality, "Kathmandu Metropolitian City|KathmanduMetropolitian City") ~ "Kathmandu", 
    str_detect(municipality, "Lalitpur Metropolitian City|LalitpurMetropolitian City") ~ "Lalitpur",
    str_detect(municipality, "Hetauda Sub-Metropolitian City|HetaudaSub-Metropolitian City") ~ "Hetauda",
    str_detect(municipality, "Bharatpur Metropolitian City|BharatpurMetropolitian City") ~ "Bharatpur",
    str_detect(municipality, "PokharaMetropolitian City") ~ "Pokhara", 
    municipality == "Manang Ngisyang" ~ "Ngisyang", 
    municipality == "Pokhara Metropolitian City" ~ "Pokhara", 
    TRUE ~ municipality
  )) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  ) |> 
  select(adm3_pcode, ward, population_density))
```


```{r individual-check}
bagmati_individual |> 
  mutate_at(
    vars(total_households:child_marriage_rate_female), 
    ~ as.numeric(.x)
  ) |> 
  mutate(population_total_check = population_urban + population_peri_urban + population_rural) |> 
  select(province, district, municipality, ward, 
         population_total, 
         total_all_ages,
         population_total_check) |> 
  mutate(difference = population_total + total_all_ages - (population_total_check * 2)) |> 
  filter(difference != 0)

gandaki_individual |> 
  mutate_at(
    vars(total_households:child_marriage_rate_female), 
    ~ as.numeric(.x)
  ) |> 
  mutate(population_total_check = population_urban + population_peri_urban + population_rural) |> 
  select(province, district, municipality, ward, 
         population_total, 
         total_all_ages,
         population_total_check) |> 
  mutate(difference = population_total + total_all_ages - (population_total_check * 2)) |> 
  filter(difference != 0)
```



```{r}
bagmati_gandaki_individual <- rbind(
  bagmati_individual, gandaki_individual
) |> 
   mutate(municipality = str_remove_all(municipality, "Gaunpalika|Municipality"),
         district = str_to_title(district),
         municipality = str_trim(municipality), 
         district = ifelse(district == "Nawalparasi (East)", 
                           "Nawalparasi East", 
                           district)) |> 
  mutate(municipality = case_when(
    municipality == "Melanchi" ~ "Melamchi", 
    str_detect(municipality, "Kathmandu Metropolitian City|KathmanduMetropolitian City") ~ "Kathmandu", 
    str_detect(municipality, "Lalitpur Metropolitian City|LalitpurMetropolitian City") ~ "Lalitpur",
    str_detect(municipality, "Hetauda Sub-Metropolitian City|HetaudaSub-Metropolitian City") ~ "Hetauda",
    str_detect(municipality, "Bharatpur Metropolitian City|BharatpurMetropolitian City") ~ "Bharatpur",
    str_detect(municipality, "PokharaMetropolitian City") ~ "Pokhara", 
    municipality == "Manang Ngisyang" ~ "Ngisyang", 
    municipality == "Pokhara Metropolitian City" ~ "Pokhara", 
    TRUE ~ municipality
  )) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  ) |> 
  left_join(
    population_densities |> 
      mutate(ward = as.character(ward)), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(
     read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv") |> 
  select(adm2_pcode, adm3_pcode, ward, rdna_affected) |> 
  mutate(rdna_affected = ifelse(rdna_affected == 0, NA_real_, rdna_affected), 
         ward = as.character(ward)), 
  by = c("adm2_pcode", "adm3_pcode", "ward")
  ) |> 
  relocate(rdna_affected, .after = ward)
```

```{r}
read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv") |> 
  select(adm2_pcode, adm3_pcode, ward, rdna_affected) |> 
  mutate(rdna_affected = ifelse(rdna_affected == 0, NA_real_, rdna_affected), 
         ward = as.character(ward)) |> 
  count(adm2_pcode)
```





## Preparation 

### Wide



```{r}
# Ward-level households wide
bagmati_gandaki_hhd  |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward != "All wards") |>
  mutate_at(vars(total_households:house_quality_least_adequate_pc), 
            ~as.numeric(.x)) |>
  mutate(ward = as.numeric(ward)) |> 
  write_csv("./data/nepal_census2021_ward_level_household_tables_bagmati_gandaki_flat.csv")

# Municipal households wide
bagmati_gandaki_hhd |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward == "All wards") |>
  mutate_at(vars(total_households:house_quality_least_adequate_pc), 
            ~as.numeric(.x)) |>
  select(-ward) |> 
  write_csv("./data/nepal_census2021_municipal_level_household_tables_bagmati_gandaki_flat.csv")

```


```{r}
# Ward-level individual wide
bagmati_gandaki_individual |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  mutate_at(vars(population_total:population_density), 
            ~as.numeric(.x)) |> 
  rename(non_agriculturual_employment_pc_male = non_agriculrual_employment_pc_male) |> 
  filter(ward != "All Wards") |> 
  mutate(ward = as.numeric(ward)) |> 
  write_csv("./data/nepal_census2021_ward_level_individual_tables_bagmati_gandaki_flat.csv")

# Municipal individual wide
bagmati_gandaki_individual |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  mutate_at(vars(population_total:population_density), 
            ~as.numeric(.x)) |> 
  rename(non_agriculturual_employment_pc_male = non_agriculrual_employment_pc_male) |> 
  filter(ward == "All Wards") |>
  select(-ward) |> 
  write_csv("./data/nepal_census2021_municipal_level_individual_tables_bagmati_gandaki_flat.csv")
  
```



### Long


```{r}
# Ward-level household long
bagmati_gandaki_hhd |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward != "All wards") |>
  mutate_at(vars(total_households:house_quality_least_adequate_pc), 
            ~as.numeric(.x)) |> 
  pivot_longer(
    cols = total_households:house_quality_least_adequate_pc, 
    names_to = "variable", 
    values_to = "value"
  ) |> 
  mutate(theme = case_when(
    str_detect(variable, "cooking_fuel") ~ "cooking fuel", 
    str_detect(variable, "drinking_water") ~ "drinking water", 
    str_detect(variable, "floor|roof|foundation|home_ownership|house_quality|outer_wall") ~ 
      "housing", 
    str_detect(variable, "hh_amenities") ~ "household amenities", 
    str_detect(variable, "lighting") ~ "lighting fuel", 
    str_detect(variable, "toilet") ~ "sanitation", 
    str_detect(variable, "total_households") ~ "demographics", 
    str_detect(variable, "wealth_quintile") ~ "wealth quintile", 
    TRUE ~ NA_character_
  )) |> 
  relocate(theme, .after = ward) |>
  mutate(ward = as.numeric(ward)) |> 
  write_csv("./data/nepal_census2021_ward_level_household_tables_bagmati_gandaki_long.csv")

# Municipal-level household long
bagmati_gandaki_hhd |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward == "All wards") |>
  mutate_at(vars(total_households:house_quality_least_adequate_pc), 
            ~as.numeric(.x)) |> 
  pivot_longer(
    cols = total_households:house_quality_least_adequate_pc, 
    names_to = "variable", 
    values_to = "value"
  ) |> 
  mutate(theme = case_when(
    str_detect(variable, "cooking_fuel") ~ "cooking fuel", 
    str_detect(variable, "drinking_water") ~ "drinking water", 
    str_detect(variable, "floor|roof|foundation|home_ownership|house_quality|outer_wall") ~ 
      "housing", 
    str_detect(variable, "hh_amenities") ~ "household amenities", 
    str_detect(variable, "lighting") ~ "lighting fuel", 
    str_detect(variable, "toilet") ~ "sanitation", 
    str_detect(variable, "total_households") ~ "demographics", 
    str_detect(variable, "wealth_quintile") ~ "wealth quintile", 
    TRUE ~ NA_character_
  )) |> 
  relocate(theme, .after = ward) |>
  select(-ward) |> 
  write_csv("./data/nepal_census2021_municipal_level_household_tables_bagmati_gandaki_long.csv")
```



```{r}
# Ward-level individual long
bagmati_gandaki_individual |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward != "All Wards") |> 
  mutate_at(vars(total_households:population_density), 
            ~as.numeric(.x)) |> 
  select(-total_population) |>
  pivot_longer(
    cols = total_households:population_density, 
    names_to = "variable", 
    values_to = "value") |>
  mutate(theme = case_when(
    str_detect(variable, "total_households|population_total|population_male|population_female|average_household_size|sex_ratio|population_density") ~ "demographics", 
    str_detect(variable, "10_years_and_older|economically_active|economic_activity") ~ "economic activity", 
    str_detect(variable, "all_ages|yrs") ~ "five-year age group", 
    str_detect(variable, "children_5_17|attending_school|attended_school") ~ "school attendance", 
    str_detect(variable, "15plus|literate|literacy") ~ "adult literacy", 
    str_detect(variable, "population_0_14|population_15_64|population_65plus|dependency") ~ "dependency ratios", 
    str_detect(variable, "population_5plus|education_level") ~ "education level", 
    str_detect(variable, "urban|rural|peri_urban") ~ "urbanisation", 
    str_detect(variable, "population_20_24|married|marriage") ~ "child marriage", 
    str_detect(variable, "disability|disabilities") ~ "disabilities",
    str_detect(variable, "agricultural|employed_population") ~ "agricultural employment", 
    TRUE ~ NA_character_
  )) |> 
  relocate(theme, .before = variable) |> 
  mutate(ward = as.numeric(ward)) |> 
  write_csv("./data/nepal_census2021_ward_level_individual_tables_bagmati_gandaki_long.csv")

# Municipal individual long
bagmati_gandaki_individual |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward == "All Wards") |> 
  mutate_at(vars(total_households:population_density), 
            ~as.numeric(.x)) |> 
  select(-total_population) |>
  pivot_longer(
    cols = total_households:population_density, 
    names_to = "variable", 
    values_to = "value") |>
  mutate(theme = case_when(
    str_detect(variable, "total_households|population_total|population_male|population_female|average_household_size|sex_ratio|population_density") ~ "demographics", 
    str_detect(variable, "10_years_and_older|economically_active|economic_activity") ~ "economic activity", 
    str_detect(variable, "all_ages|yrs") ~ "five-year age group", 
    str_detect(variable, "children_5_17|attending_school|attended_school") ~ "school attendance", 
    str_detect(variable, "15plus|literate|literacy") ~ "adult literacy", 
    str_detect(variable, "population_0_14|population_15_64|population_65plus|dependency") ~ "dependency ratios", 
    str_detect(variable, "population_5plus|education_level") ~ "education level", 
    str_detect(variable, "urban|rural|peri_urban") ~ "urbanisation", 
    str_detect(variable, "population_20_24|married|marriage") ~ "child marriage", 
    str_detect(variable, "disability|disabilities") ~ "disabilities", 
    str_detect(variable, "agricultural|employed_population") ~ "agricultural employment",
    TRUE ~ NA_character_
  )) |> 
  relocate(theme, .before = variable) |> 
  select(-ward) |>
  write_csv("./data/nepal_census2021_municipal_level_individual_tables_bagmati_gandaki_long.csv")
  
```




```{r}
bagmati_gandaki_hhd |> 
  filter(district %in% c("Nuwakot", "Rasuwa", "Dhading", "Chitawan", "Tanahu", "Gorkha")) |> 
  filter(municipality %in% c("Aamachhodingmo", "Aanbu Khaireni", 
                             "Belkotgadhi", "Benighat Rorang", 
                             "Bidur", "Devghat", "Gajuri", "Galchhi", 
                             "Ichchha Kamana", "Gosaikunda", "Kalika", 
                             "Kispang", "Siddhalek", "Tarakeshwor", 
                             "Uttargaya", "Gandaki", "Shahid Lakhan")) |>
  select(province, district, municipality, adm1_pcode, adm2_pcode, adm3_pcode, 
         ward) |> 
  filter(ward != "All wards") |> 
  write_csv("./data/affected_wards.csv")
  count(municipality)
```

### Filtered

```{r}
match <- read_xls("./data/Affected_wardsv2.xls") |> 
  janitor::clean_names() |> 
  select(adm1_pcode, 
         district = adm2_en, 
         adm2_pcode,
         municipality = adm3_en, 
         adm3_pcode, 
         ward = new_ward_n) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = "adm1_pcode"
  ) |> 
  rename(province = adm1_name) |> 
  relocate(province, .before = adm1_pcode) |> 
  mutate(match = paste0(adm1_pcode, adm2_pcode, adm3_pcode, ward))

match_list <- match$match
```


```{r}
# Ward-level households wide
bagmati_gandaki_hhd  |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward != "All wards") |>
  mutate_at(vars(total_households:house_quality_least_adequate_pc), 
            ~as.numeric(.x)) |>
  mutate(ward = as.numeric(ward)) |> 
  mutate(match = paste0(adm1_pcode, adm2_pcode, adm3_pcode, ward)) |> 
  filter(match %in% match_list) |> 
  select(-match) |> 
  write_csv("./data/FILTERED_nepal_census2021_ward_level_household_tables_bagmati_gandaki_flat.csv")

# Ward-level individual wide
bagmati_gandaki_individual |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  mutate_at(vars(population_total:population_density), 
            ~as.numeric(.x)) |> 
  filter(ward != "All Wards") |> 
  mutate(ward = as.numeric(ward)) |> 
  mutate(match = paste0(adm1_pcode, adm2_pcode, adm3_pcode, ward)) |> 
  filter(match %in% match_list) |> 
  select(-match) |> 
  write_csv("./data/FILTERED_nepal_census2021_ward_level_individual_tables_bagmati_gandaki_flat.csv")

# Ward-level household long
bagmati_gandaki_hhd |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward != "All wards") |>
  mutate_at(vars(total_households:house_quality_least_adequate_pc), 
            ~as.numeric(.x)) |> 
  pivot_longer(
    cols = total_households:house_quality_least_adequate_pc, 
    names_to = "variable", 
    values_to = "value"
  ) |> 
  mutate(theme = case_when(
    str_detect(variable, "cooking_fuel") ~ "cooking fuel", 
    str_detect(variable, "drinking_water") ~ "drinking water", 
    str_detect(variable, "floor|roof|foundation|home_ownership|house_quality|outer_wall") ~ 
      "housing", 
    str_detect(variable, "hh_amenities") ~ "household amenities", 
    str_detect(variable, "lighting") ~ "lighting fuel", 
    str_detect(variable, "toilet") ~ "sanitation", 
    str_detect(variable, "total_households") ~ "demographics", 
    str_detect(variable, "wealth_quintile") ~ "wealth quintile", 
    TRUE ~ NA_character_
  )) |> 
  relocate(theme, .after = ward) |>
  mutate(ward = as.numeric(ward)) |> 
  mutate(match = paste0(adm1_pcode, adm2_pcode, adm3_pcode, ward)) |> 
  filter(match %in% match_list) |> 
  select(-match) |> 
  write_csv("./data/FILTERED_nepal_census2021_ward_level_household_tables_bagmati_gandaki_long.csv")

# Ward-level individual long
bagmati_gandaki_individual |> 
  relocate(adm1_pcode, .before = ward) |> 
  relocate(adm2_pcode, .after = adm1_pcode) |> 
  relocate(adm3_pcode, .after = adm2_pcode) |> 
  filter(ward != "All Wards") |> 
  mutate_at(vars(total_households:population_density), 
            ~as.numeric(.x)) |> 
  select(-total_population) |>
  pivot_longer(
    cols = total_households:population_density, 
    names_to = "variable", 
    values_to = "value") |>
  mutate(theme = case_when(
    str_detect(variable, "total_households|population_total|population_male|population_female|average_household_size|sex_ratio|population_density") ~ "demographics", 
    str_detect(variable, "10_years_and_older|economically_active|economic_activity") ~ "economic activity", 
    str_detect(variable, "all_ages|yrs") ~ "five-year age group", 
    str_detect(variable, "children_5_17|attending_school|attended_school") ~ "school attendance", 
    str_detect(variable, "15plus|literate|literacy") ~ "adult literacy", 
    str_detect(variable, "population_0_14|population_15_64|population_65plus|dependency") ~ "dependency ratios", 
    str_detect(variable, "population_5plus|education_level") ~ "education level", 
    str_detect(variable, "urban|rural|peri_urban") ~ "urbanisation", 
    str_detect(variable, "population_20_24|married|marriage") ~ "child marriage", 
    str_detect(variable, "disability|disabilities") ~ "disabilities", 
    TRUE ~ NA_character_
  )) |> 
  relocate(theme, .before = variable) |> 
  mutate(ward = as.numeric(ward)) |> 
  mutate(match = paste0(adm1_pcode, adm2_pcode, adm3_pcode, ward)) |> 
  filter(match %in% match_list) |> 
  select(-match) |> 
  write_csv("./data/FILTERED_nepal_census2021_ward_level_individual_tables_bagmati_gandaki_long.csv")
```


### Missing

The areas missing from the census seem to be largely uninhabited (entirely mountainous) or are nature reserves, in the case of Chitawan

```{r}
nepal_admin |> 
  filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
  count(adm3_pcode, adm3_name) |> 
  left_join(
    bagmati_gandaki_hhd |> 
      distinct(adm3_pcode, municipality),
    by = "adm3_pcode"
  ) |> 
  filter(is.na(municipality))
  
```

```{r}
adm3 |>
  filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
  mutate(missing = ifelse(adm3_pcode %in% c("NP0328597", 
                                            "NP0331595", 
                                            "NP0331597", 
                                            "NP0335597", 
                                            "NP0444598", 
                                            "NP0447597"), 
                          1, 0)) |> 
  st_as_sf() |> 
  ggplot() +
  geom_sf(aes(fill = missing))
```

```{r}
read_xlsx("./data/census/Indv_Bagmati_EmpSectorHldNonHldAllageSex_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_20_24_total", 
             "population_20_24_male", 
             "population_20_24_female", 
             "population_married_before_18_total", 
             "population_married_before_18_male", 
             "population_married_before_18_female", 
             "child_marriage_rate_total", 
             "child_marriage_rate_male", 
             "child_marriage_rate_female")) |> 
```


```{r}
read_xlsx("./data/census/WRD_Bagmati_Indv01-HouseholdAndPopulation.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "total_households",
             "population_total", 
             "population_male",
             "population_female",
             "average_household_size", 
             "sex_ratio")) |> 
  ward_fill_filter() 
  select(-province, -district, -municipality, -ward)
```

```{r}


read_xlsx("./data/census/WRD_Bagmati_Indv05-EconomicActivity.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", "sex", "total_population",
             "total_population_10_years_and_older",
             "economically_ative_usually_employed",
             "economically_active_usually_unemployed", 
             "not_usually_economically_active", 
             "not_economically_active", 
             "economic_activity_not_stated")) |> 
  ward_fill_filter2() |> 
  filter(!is.na(sex)) |> 
  mutate(sex = str_to_lower(sex)) |> 
  pivot_wider(
    names_from = c("sex"), 
    values_from = c("total_population",
                    "total_population_10_years_and_older", 
                    "economically_ative_usually_employed", 
                    "economically_active_usually_unemployed", 
                    "not_usually_economically_active", 
                    "not_economically_active"), 
    names_glue ="{sex}_{.value}"
  ) |> 
  rename(economically_active_surveyed_population = total_total_population, 
         economically_active_surveyed_male_population = male_total_population, 
         economically_active_surveyed_female_population = female_total_population, 
         total_population_10_years_and_older = total_total_population_10_years_and_older, 
         male_population_10_years_and_older = male_total_population_10_years_and_older, 
         female_population_10_years_and_older = female_total_population_10_years_and_older)
  glimpse()


```

### Working

#### Municipal differences 

```{r}
bagmati_gandaki_individual <- read_csv("./data/nepal_census2021_ward_level_individual_tables_bagmati_gandaki_flat.csv")

differences <- read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv")

differences_match <- differences |> 
      mutate(match = paste0(adm2_pcode, adm3_pcode, ward)) |> 
      filter(rdna_affected == 1) |> 
  pull(match)

bagmati_gandaki_individual |>
  mutate(match = paste0(adm2_pcode, adm3_pcode, ward)) |> 
  select(district, municipality, ward, population_total, match) |> 
  filter(match %in% differences_match) |> 
  group_by(district, municipality) |> 
  summarise(population_affected_wards_census = sum(population_total), 
            .groups = "drop") |> 
  left_join(
    municipal_damage_losses |>
      filter(!is.na(population_in_affected_wards_census_2021)) |>
      select(district, municipality, population_rdna_presentation = population_in_affected_wards_census_2021), 
    by = c("district", "municipality")
  ) |> 
  mutate(difference = population_affected_wards_census - population_rdna_presentation) |> 
  write_csv("./data/municipal_differences_rdna_census.csv")

```




```{r}
read_csv("./data/FILTERED_nepal_census2021_ward_level_individual_tables_bagmati_gandaki_flat.csv") |> 
  summarise(total_households = sum(total_households, na.rm = TRUE), 
            population_total = sum(population_total, na.rm = TRUE))
  glimpse()
  filter(total_households, )
  glimpse()
  
  223574 / 56550
```


```{r}
read_xlsx("./data/census/WRD_Bagmati_Indv02-FiveYearsAgeGroupsAndSex.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "ward", 
             "five_year_age_group", 
             "total",
             "male", 
             "female")) |> 
  ward_fill_filter2() |> 
  filter(!is.na(five_year_age_group)) |> 
  mutate(five_year_age_group = str_replace(five_year_age_group, "-| ", "_"), 
         five_year_age_group = str_to_lower(five_year_age_group),
         five_year_age_group = str_replace(five_year_age_group, " yrs.", "_yrs"), 
         five_year_age_group = str_remove(five_year_age_group, "\\."), 
         five_year_age_group = str_replace(five_year_age_group, "\\+", "plus")) |> 
  pivot_wider(
    names_from = "five_year_age_group", 
    values_from = c("total", "male", "female"), 
    names_glue = "{.value}_{five_year_age_group}"
  ) 
```

```{r}
read_xlsx("./data/census/Indv_Bagmati_educationaStatusChild_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
      "total_children_5_17", 
      "male_children_5_17", 
      "female_children_5_17", 
      "currently_attending_school_male", 
      "currently_attending_school_female", 
      "oos_ever_attended_school_male", 
      "oos_ever_attended_school_female", 
      "oos_never_attended_school_male", 
      "oos_never_attended_school_female", 
      "currently_attending_school_total_pc", 
      "currently_attending_school_male_pc", 
      "currently_attending_school_female_pc", 
      "oos_ever_attended_school_total_pc", 
      "oos_ever_attended_school_male_pc", 
      "oos_ever_attended_school_female_pc", 
      "oos_never_attended_school_total_pc", 
      "oos_never_attended_school_male_pc", 
      "oos_never_attended_school_female_pc")
  ) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  glimpse()
  
```



```{r}
read_xlsx("./data/census/Indv_Bagmati_Adultliteracy15plus_Ward.xlsx", skip = 2) |> 
  setNames(
    c("province", "district", "municipality", "name", "ward",
      "population_15plus_total",
      "population_15plus_male", 
      "population_15plus_female", 
      "literate_population_total", 
      "literate_population_male", 
      "literate_population_female", 
      "literacy_rate_total", 
      "literacy_rate_male", 
      "literacy_rate_female"
      )
  ) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |>
  glimpse()
  
```

```{r}
read_xlsx("./data/census/Indv_Bagmati_BroadAge_dependency_ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_0_14", 
             "population_15_64", 
             "population_65plus", 
             "total_population", 
             "child_dependency_ratio", 
             "elderly_dependency_ratio",  
             "total_dependency_ratio")) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  glimpse()
```


```{r}
read_xlsx("./data/census/Indv_Bagmati_educationalLevel_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_5plus_total", 
             "population_5plus_male", 
             "population_5plus_female", 
             "education_level_illiterate_male", 
             "education_level_illiterate_female", 
             "education_level_early_childhood_male", 
             "education_level_early_childhood_female", 
             "education_level_basic_level_male", 
             "education_level_basic_level_female", 
             "education_level_secondary_male", 
             "education_level_secondary_female", 
             "education_level_higher_education_male", 
             "education_level_higher_education_female", 
             "education_level_other_male", 
             "education_level_other_female", 
             "education_level_illiterate_pc_total", 
             "education_level_illiterate_pc_male", 
             "education_level_illiterate_pc_female", 
             "education_level_early_childhood_pc_total", 
             "education_level_early_childhood_pc_male", 
             "education_level_early_childhood_pc_female", 
             "education_level_basic_level_pc_total", 
             "education_level_basic_level_pc_male", 
             "education_level_basic_level_pc_female", 
             "education_level_secondary_pc_total", 
             "education_level_secondary_pc_male", 
             "education_level_secondary_pc_female", 
             "education_level_higher_education_pc_total",
             "education_level_higher_education_pc_male", 
             "education_level_higher_education_pc_female", 
             "education_level_other_pc_total", 
             "education_level_other_pc_male", 
             "education_level_other_pc_female"
             )) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  glimpse()
```


```{r}
read_xlsx("./data/census/Indv_Bagmati_DegreeOfUrbanization_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_total", 
             "population_male", 
             "population_female",
             "population_urban", 
             "population_peri_urban",
             "population_rural", 
             "population_pc_urban", 
             "population_pc_peri_urban", 
             "population_pc_rural")) |> 
  bagmati_district_names() |> 
  glimpse()
```

```{r}
read_xlsx("./data/census/Indv_Bagmati_ChildmariageBefore18_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "population_20_24_total", 
             "population_20_24_male", 
             "population_20_24_female", 
             "population_married_before_18_total", 
             "population_married_before_18_male", 
             "population_married_before_18_female", 
             "child_marriage_rate_total", 
             "child_marriage_rate_male", 
             "child_marriage_rate_female")) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  glimpse()
```

```{r}
read_xlsx("./data/census/Indv_Bagmati_disability_Ward.xlsx", skip = 2) |> 
  setNames(c("province", "district", "municipality", "name", "ward",
             "total_population", 
             "population_with_disabilities", 
             "population_without_disabilities", 
             "population_disability_not_reported", 
             "disability_prevlance_rate")) |> 
  ward_fill_filter() |> 
  bagmati_district_names() |> 
  glimpse()
```




```{r}


|> 
  mutate(district = ifelse(district == "Nawalparasi (East)", "Nawalparasi East", district)) |>
  mutate(municipality = str_remove_all(municipality, "Gaunpalika|Municipality"), 
         municipality = str_trim(municipality)) |> 
  mutate(municipality = case_when(
    municipality == "Melanchi" ~ "Melamchi", 
    municipality == "Kathmandu Metropolitian City" ~ "Kathmandu", 
    municipality == "Lalitpur Metropolitian City" ~ "Lalitpur", 
    municipality == "Hetauda Sub-Metropolitian City" ~ "Hetauda", 
    municipality == "Bharatpur Metropolitian City" ~ "Bharatpur", 
    municipality == "Manang Ngisyang" ~ "Ngisyang", 
    municipality == "Pokhara Metropolitian City" ~ "Pokhara", 
    TRUE ~ municipality
  )) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  )
```


```{r}
affected_wards |> 
  select(adm2_en, adm2_pcode, adm3_en, new_ward_n) |> 
  left_join(nepal_admin |> 
              distinct(adm1_name, adm2_pcode), 
            by = "adm2_pcode") |> 
  select(adm1_en = adm1_name, adm2_en, adm3_en, ward_number = new_ward_n) |> 
  count(adm1_en)
  write_csv("./data/locations_assessment_registry.csv")

nepal_admin |> 
  filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
  distinct(adm1_name, adm2_name, adm3_name, adm1_pcode, adm2_pcode, adm3_pcode) |> 
  write_csv("./data/locations_assessment_registry.csv")
 
```



```{r}

affected_wards_population |> 
  mutate(count = 1) |> 
  group_by(district) |> 
  summarise(municipalities = n_distinct(adm3_pcode), 
            municipalities_emergency = sum(count[emergency_declared == "Yes"], na.rm = TRUE), 
            affected_population = sum(estimated_affected_population)) |> 
  rename(`Affected Population` = affected_population, 
         `Municipalities declared emergency` = municipalities_emergency, 
         District = district, 
         Municipalities = municipalities) |> 
  arrange(desc(`Affected Population`)) |> 
  flextable() %>% 
  set_caption(caption = "Affected population by municipality") %>% 
  theme_zebra() |> 
  save_as_image("./plots/affected_population_municipality.png")
```

# FODs

## Functions

```{r}
clean_district_municipality <- function(tbl) {
 
   tbl |> 
    mutate(district = ifelse(district == "Chitwan", "Chitawan", district), 
         municipality = case_when(
           str_detect(municipality, "Ichchhyakamana") ~ "Ichchha Kamana", 
           str_detect(municipality, "Galchi") ~ "Galchhi",
           str_detect(municipality, "Sahid Lakhan") ~ "Shahid Lakhan", 
           str_detect(municipality, "Tarkeshwar") ~ "Tarakeshwor",
           str_detect(municipality, "Sidhhalek") ~ "Siddhalek", 
           str_detect(municipality, "Belkotgadi") ~ "Belkotgadhi", 
           TRUE ~ municipality
         )) |> 
    left_join(
    nepal_admin |> 
      distinct(adm2_name, adm2_pcode, adm3_name, adm3_pcode), 
    by = c("district" = "adm2_name", 
           "municipality" = "adm3_name")
  )
}

```


```{r}
damage <- read_xlsx("./data/Consolidated Damage.xlsx") |> 
  janitor::clean_names() |> 
  glimpse()
```

```{r}
# Household impacts 
household_impacts <- 

```

## Sector damage and losses


```{r}
sector_damage_and_losses <- read_xlsx("./data/RDNA tables.xlsx", 
          sheet = "damage_and_losses") |> 
  clean_names() |> 
  rename_all(~str_replace_all(.x, "us_million", "usd_million")) |> 
  rename_all(~str_replace_all(.x, "months_npr", "months_npr_crore")) |> 
  rename(sub_sector = sector) |> 
  mutate(sub_sector = str_extract(sub_sector, "[A-Za-z\\s]+"), 
         sub_sector = str_trim(str_to_lower(sub_sector))) |> 
  mutate(sector = case_when(
    sub_sector %in% c("private buildings", "public buildings and facilities", 
                      "education", "health", "cultural heritage") ~ "social", 
    sub_sector %in% c("agriculture", "fisheries", "livestock", 
                      "banking", "economic activities") ~ "productive", 
    sub_sector %in% c("energy", "household renewable energy", 
                      "roads", "bridges", "telecommunication", "wash", 
                      "irrigation and river training") ~ "infrastructure", 
    sub_sector %in% c("debris", "disaster risk reduction", 
                      "inclusive recovery") ~ "cross cutting", 
    TRUE ~ "subtotal"
  )) |> 
  filter(sector != "subtotal") |> 
  mutate(sub_sector = case_when(
    sub_sector == "energy" ~ "energy, hydropower and grid", 
    sub_sector == "economic activities" ~ "economic activities and livelihooods", 
    TRUE ~ sub_sector
  )) |> 
  mutate_at(vars(damages_npr_crore:total_recovery_needs_npr_crore), 
            ~parse_number(.x)) |> 
  relocate(sector, .before = sub_sector)

# There are spaces after each of the numbers in the excel tables
# This renders them unusable
damage_and_losses %>%
  {sum(.$total_recovery_needs_npr_crore, na.rm = TRUE)}

sector_damage_and_losses |> 
  write_csv("./data/sector_damage_and_losses.csv")
```




## Municipal damage and losses

```{r}
impacted_buildings |> 
  filter(municipality == "Benighat Rorang")
  glimpse()
```


```{r}
ward_cadastral |> 
  filter(municipality == "Gosaikunda")
```


```{r}
ward_cadastral <- rbind(
  read_xlsx("./data/RDNA tables.xlsx", sheet = "rasuwa_cadastral") |> 
  clean_names() |> 
  rename(municipality = municipality_cbs_name) |> 
  mutate(municipality = str_remove_all(municipality, "\\ "), 
         municipality = str_remove_all(municipality, "Rural|RuralMunicipality|Municipality"), 
         municipality = str_trim(municipality), 
         municipality = case_when(
           municipality == "Aamachaodingmo" ~ "Aamachhodingmo",
           municipality == "Gosainkunda" ~ "Gosaikunda", 
           TRUE ~ municipality), 
         district = "Rasuwa") |> 
  mutate_at(vars(ward:affected_cadastral_area_as_percent_of_ward_area), 
            ~ parse_number(.x)) |> 
  mutate(affected_cadastral_area_as_percent_of_ward_area = affected_cadastral_area_as_percent_of_ward_area / 100) |> 
  clean_district_municipality() |> 
  filter(municipality != "TOTAL"), 
 
 read_xlsx("./data/RDNA tables.xlsx", sheet = "nuwakot_cadastral") |> 
  clean_names() |> 
  rename(municipality = municipalit_y_cbs_nam_e) |> 
  mutate(municipality = str_remove_all(municipality, "\\ "), 
         municipality = str_remove_all(municipality, "Rural|RuralMunicipality|Municipality"), 
         municipality = str_trim(municipality),
         district = "Nuwakot") |>
  mutate_at(vars(ward:affected_cadastral_area_as_percent_of_ward_area), 
            ~ parse_number(.x)) |> 
  mutate(affected_cadastral_area_as_percent_of_ward_area = affected_cadastral_area_as_percent_of_ward_area / 100) |> 
  clean_district_municipality() |> 
  filter(municipality != "TOTAL")
 )
  
```

```{r}
municipal_damage_losses <- nepal_admin |> 
  filter(adm2_name %in% c("Nuwakot", "Rasuwa", "Dhading", "Chitawan", "Tanahu", "Gorkha")) |> 
  distinct(adm2_name, adm2_pcode, adm3_name, adm3_pcode) |> 
  rename(district = adm2_name, municipality = adm3_name) |> 
  left_join(
    read_xlsx("./data/RDNA tables.xlsx", 
          sheet = "impacted_hhds") |> 
      janitor::clean_names() |> 
      filter(!is.na(affected_wards)) |> 
      rename(households_in_affected_wards_census_2021 = household_in_affeced_wards_census_2021, 
             household_size_census_2021 = househol_d_size_census_2021, 
             municipality = district_local) |> 
      mutate_at(vars(households_in_affected_wards_census_2021:household_size_census_2021), 
                ~ parse_number(.x)) |> 
      mutate_at(vars(district, municipality), ~str_trim(.x)) |> 
      mutate(district = str_to_title(district), 
             number_of_affected_wards = str_count(affected_wards, ",") + 1) |> 
      relocate(number_of_affected_wards, .after = affected_wards) |> 
      clean_district_municipality() |> 
      select(-district, -municipality) |> 
      mutate(household_damage = 1),
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  left_join(
    read_xlsx("./data/RDNA tables.xlsx", sheet = "composition_of_damage") |>
      clean_names() |>
      rename(district = x1, municipality = district_local_level) |>
      mutate_at(vars(affected_buildings:rcc_other), ~ parse_number(.x)) |>
      mutate_at(vars(district, municipality), ~ str_trim(.x)) |>
      filter(municipality != "Total") |> 
      clean_district_municipality() |> 
      select(-district, -municipality),
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  left_join(
    read_xlsx("./data/RDNA tables.xlsx", sheet = "crop_damage") |> 
      clean_names() |> 
      mutate(municipality = str_extract(municipality, "[^/]+$"), 
             municipality = str_trim(municipality)) |> 
      clean_district_municipality() |> 
      filter(municipality != "Grand Total") |>
      mutate_at(vars(paddy_baseline_hectares:vegetables_affected_hectares), 
                ~ parse_number(.x)) |> 
      mutate(crop_damage = 1) |> 
      select(-district, -municipality), 
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  left_join(
    read_xlsx("./data/RDNA tables.xlsx", sheet = "agricultural_damage") |> 
      clean_names() |> 
      rename(municipality = local_level) |> 
      mutate(district = case_when(
        str_detect(municipality, "Aanbu Khaireni|Bandipur|Devghat") ~ "Tanahu",
        str_detect(municipality, "Belkotgadi|Bidur|Likhu") ~ "Nuwakot", 
        str_detect(municipality, "Benighat Rorang|Gajuri|Galchhi|Sidhhalek") ~ "Dhading", 
        str_detect(municipality, "Bharatpur|Ichchha Kamana") ~ "Chitawan", 
        str_detect(municipality, "Gandaki|Shahid Lakhan") ~ "Gorkha", 
        str_detect(municipality, "Gosaikunda|Uttargaya") ~ "Rasuwa",
        TRUE ~ NA_character_
      )) |> 
      mutate(district = str_trim(district), 
             municipality = str_trim(municipality)) |> 
      clean_district_municipality() |> 
      mutate_at(vars(total_no_of_holdings:temporary_crop_holdings_number), 
                ~parse_number(.x)) |> 
      mutate(agricultural_damage = 1) |> 
      select(-district, -municipality), 
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  left_join(
    # Aligns with household impacts
    read_xlsx("./data/RDNA tables.xlsx", sheet = "business_exposure") |> 
      clean_names() |> 
      mutate_at(vars(district, municipality), ~ str_trim(.x)) |>
      clean_district_municipality() |>  
      rename(damage_corridor_buildings = corridor_buildings) |> 
      mutate_at(vars(damage_corridor_buildings:building_impact_share), 
                ~parse_number(.x)) |>
      mutate(building_impact_share = building_impact_share / 100) |> 
      filter(municipality != "Total") |> 
      mutate(business_exposure = 1)|> 
      select(-district, -municipality, -impacted_buildings), 
    by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  left_join(
    ward_cadastral |> 
      group_by(adm2_pcode, adm3_pcode) |> 
      summarise(
        affected_cadastral_parcels = sum(no_of_affected_cadastral_parcels, na.rm = TRUE), 
        affected_hectares = sum(total_ward_area_hectares, na.rm = TRUE), 
        affected_hectares_cadastral = sum(total_affected_cadastral_area_hectares, na.rm = TRUE), 
        .groups = "drop") |> 
      mutate(cadastral_damage = 1), 
    by = c("adm2_pcode", "adm3_pcode")
  )

municipal_damage_losses |> 
  mutate(affected_wards = str_trim(affected_wards)) |> 
  filter(household_damage == 1 | crop_damage == 1 | agricultural_damage == 1 |
           business_exposure == 1 | cadastral_damage == 1) |> 
  write_csv("./data/municipal_damage_loss.csv")

```



```{r}
municipal_damage_losses |> 
  filter(household_damage == 1 | crop_damage == 1 | agricultural_damage == 1 |
           business_exposure == 1 | cadastral_damage == 1) |> 
  glimpse()
  filter(municipality == "Likhu")
  select(impacted_buildings.x, impacted_buildings.y)
```

This was for the humanitarian snapshot 

```{r}
municipal_damage_losses |> 
  select(district, municipality, impacted_buildings) |> 
  filter(!is.na(impacted_buildings)) |> 
  ggplot(aes(x = impacted_buildings, y = fct_reorder(municipality, impacted_buildings))) + 
  geom_col(fill = "#009edb") + 
  geom_text(aes(label = comma(impacted_buildings)),
            hjust = "inward", 
            size = 7) +
  scale_x_continuous(labels = comma, breaks = seq(0, 3500, 500)) + 
  labs(title = "Number of Impacted Buildings by Municipality", 
       x = "", y = "") +
  theme_void() +
  theme(plot.title = element_text(hjust = .5, size = 18, face = "bold"), 
        axis.text.y = element_text(size = 15, hjust = 0))
  
ggsave("./plots/number_of_affected_building_municipality.png", height = 7.5, width = 7.5, units = "in")
```


## Ward damage




# Mapping

```{r}
affected_municipalities_wards |> 
  left_join(
    wards, 
    by = c("adm3_pcode", "ward" = "NEW_WARD_N")
  ) |> 
  st_as_sf() |> 
  ggplot() +
  geom_sf(fill = "lightblue") + 
  geom_sf(data = adm3 |> filter(adm3_pcode %in% affected_municipalities_wards$adm3_pcode), 
          alpha = .1) +
  geom_sf_text(data = adm3 |> filter(adm3_pcode %in% affected_municipalities_wards$adm3_pcode),
               aes(label = adm3_name), 
               size = 2, 
               colour = "red")
  glimpse()

```

Play with rasters later

```{r}

bbox <- st_bbox(c(xmin = 80.0667, xmax = 88.2000, ymin = 26.3667,  ymax = 30.4500), 
                crs = st_crs(faded_country))

faded_country <- st_read("./data/shapefiles/npl_carto_fea_py_mapaction_pp_faded_country.shp")

st_crop(faded_country, bbox) |> 
  glimpse()

st_crop(faded_country, bbox) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf()
  glimpse()
  
X Range (West to East): 80.0667 to 88.2000Y Range (South to North): 26.3667 to 30.4500  

faded_country |> glimpse()

st_crs(faded_country)
```


# 5Ws

## Deduplication 

```{r}
all_duplicates <- consolidated |> 
  left_join(
    consolidated |>
      # filter(lead_agency %in% c("UNICEF")) |>
      filter(individuals_reached > 0) |>
      count(province,
            district,
            municipality,
            ward,
            sector, 
            activity,
            individuals_reached,
            sort = TRUE) |>
      rename(duplicates = n) |> 
      mutate(duplicates = ifelse(duplicates < 2, NA_real_, duplicates)),
    
    by = c("province", "district", "municipality", "ward",
           "sector", "activity", "individuals_reached")
  )  |> 
  # filter(duplicates > 1) |> 
  arrange(duplicates, province, district, municipality, lead_agency, implementing_partner)

all_duplicates |> 
  # writexl::write_xlsx("./data/all_duplicates_consolidated.xlsx")
  count(duplicates)

```



```{r}
consolidated |> 
  left_join(
    consolidated |>
      filter(lead_agency %in% c("UNICEF")) |>
      filter(individuals_reached > 0) |>
      count(province,
            district,
            municipality,
            ward,
            activity,
            individuals_reached,
            sort = TRUE) |>
      rename(duplicates = n) |> 
      mutate(duplicates = ifelse(duplicates < 2, NA_real_, duplicates), 
             unicef_duplicates = ifelse(duplicates > 1, "unicef_duplicates", NA_character_)),
    
    by = c("province", "district", "municipality", "ward",
           "activity", "individuals_reached")
  )  |> 
  filter(unicef_duplicates > 1) |> 
  arrange(province, district, municipality, lead_agency, implementing_partner)





  write_csv("./data/unicef_duplicated_rows.csv")
 
  
  glimpse()
```





## NDRRMA Summary 

```{r}
read_xlsx("./data/Nepal_Relief_items_20260919_Sudarat.xlsx") |>
  glimpse()
```

```{r}
consolidated |> 
  filter(response_modality != "Awareness/Advocacy") |> 
  group_by(province, district, municipality, sector, relief_items = relief_items_standard_in_kind_items, 
           relief_item_unit) |> 
  summarise(
    number_of_relief_items_planned = sum(number_of_relief_items_planned, na.rm = TRUE), 
    number_of_relief_items_distributed = sum(number_of_relief_items_distributed, na.rm = TRUE), 
    households_targeted = sum(households_targeted, na.rm = TRUE), 
    people_targeted = sum(people_targeted_individuals, na.rm = TRUE), 
    households_reached = sum(households_reached, na.rm = TRUE), 
    total_people_reached = sum(individuals_reached, na.rm = TRUE),
    .groups = "drop") |> 
  left_join(
    consolidated |> 
      mutate(duplicate = ifelse(implementing_partner == lead_agency, 1, 0)) |>
      mutate(implementing_partner = ifelse(duplicate == 1, NA_character_, implementing_partner)) |>
      pivot_longer(lead_agency:implementing_partner,
                   names_to = "role",
                   values_to = "agencies") |>
      filter(!is.na(agencies)) |>
      filter(!is.na(sector)) |>
      rename(relief_items = relief_items_standard_in_kind_items) |>
      distinct(province,
               district,
               municipality,
               sector,
               relief_items,
               relief_item_unit,
               agencies) |>
      group_by(province,
               district,
               municipality,
               sector,
               relief_items,
               relief_item_unit) |>
      summarise(agencies = paste0(agencies, collapse = ", ")),
    by = c("province", "district", "municipality", "sector", 
           "relief_items", "relief_item_unit")
  ) |> 
  filter(!is.na(agencies)) |> 
  glimpse()

  writexl::write_xlsx("./data/sudarat_relief_items_table_20260921.xlsx")
  write_csv("./data/sudarat_relief_items_table_20260921.csv")
```

```{r}
consolidated |> 
mutate(duplicate = ifelse(
    implementing_partner == lead_agency, 
    1, 0
  )) |> 
  mutate(implementing_partner = ifelse(
    duplicate == 1, NA_character_, implementing_partner
  )) |> 
  pivot_longer(
    lead_agency:implementing_partner, 
    names_to = "role",
    values_to = "agencies"
  ) |> 
  filter(!is.na(agencies)) |>  
  filter(!is.na(sector)) |> 
  rename(relief_items = relief_items_standard_in_kind_items) |> 
  distinct(province, district, municipality, sector, relief_items, 
           relief_item_unit, agencies) |>
  group_by(
    province, district, municipality, sector, relief_items, relief_item_unit
  ) |> 
  summarise(agencies = paste0(agencies, collapse = ", ")) 
```


```{r}
consolidated |> glimpse()
```



```{r}
consolidated2 <- read_xlsx("./data/NEPAL 5W Data Consolidation (ADMIN_ONLY) 20260917.xlsx", 
                          skip = 5, 
                          sheet = "Compiled_Data") |> 
  clean_names()

nepal_admin |> 
  filter(str_detect(adm3_name, "Langtang"))
```
```{r}
clean <- consolidated2 |>
  filter(disaster_response_plan %in% c("Rasuwa Flood Response", "Rasuwa Flood Respnese")) |> 
  mutate_at(c("province", "district", "municipality"), ~ str_to_title(.)) |> 
  mutate_at(c("province", "district", "municipality"), ~ str_trim(.)) |> 
  mutate(municipality = str_remove_all(municipality, " Gaunpalika"), 
         municipality = str_remove_all(municipality, " Municipality")) |>
  mutate(municipality = case_when(
    municipality == "Benighat" ~ "Benighat Rorang", 
    municipality == "Galchi Rural Municipality" ~ "Galchhi", 
    municipality == "Gandaki" ~ "Gandaki", 
    municipality == "Bheri Malika Municipality" ~ "Bheri Malika", 
    municipality == "Nalgad Municipality" ~ "Nalgad", 
    municipality == "Kathmandu Metropolitian City" ~ "Kathmandu", 
    municipality == "Nagarjun Municipality" ~ "Nagarjun", 
    municipality == "Belkotgadhi Municipality|Belkotgadhi Nagarpalika" ~ "Belkotgadhi", 
    str_detect(municipality, "Langtang") ~ "Langtang", 
    str_detect(municipality, "Bidur") ~ "Bidur", 
    municipality == "Kispang Municipality" ~ "Kispang", 
    municipality == "Tarkeshwor" ~ "Tarakeshwor", 
    municipality == "Rasuwa Dao, Dhunche" ~ "Gosaikunda",
    str_detect(municipality, "Devghat") ~ "Devghat", 
    str_detect(municipality, "Gandaki") ~ "Gandaki", 
    str_detect(municipality, "Belkotgadhi") ~ "Belkotgadhi", 
    str_detect(municipality, "Langtang") ~ "Langtang",
    municipality == "Aanbukhaireni" ~ "Aanbu Khaireni",
    TRUE ~ municipality)) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm3_pcode != "NP0328596") |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  )
```

```{r}
clean |> 
  mutate(adm2_error = case_when(
    district == "Nuwakot" & municipality == "Kathmandu" ~ 1,
    district == "Nuwakot, Rasuwa" ~ 1, 
    district == "Nuwakot" & municipality == "Gosaikunda" ~ 1, 
    is.na(municipality) ~ 1, 
    TRUE ~ 0
  )) |> 
  

```

```{r}
activity_check <- clean |> 
  filter(activity != "Other") |> 
  distinct(activity, activity_description) |> 
  mutate(proposed_activity = 
           case_when(
             str_detect(activity, "Cash for work") ~ 
               "Cash for Work", 
             str_detect(activity, "Multipurpose CASH support") | 
               str_detect(activity_description, "MPC distribution") ~ 
               "Multipurpose Cash Support", 
             str_detect(activity, "targeted MHPSS|Provide psychosocial support|Provision of MHPSS|psychosocial treatment") & !str_detect(activity, "PSA messaging|Capacity building|Community Sensitization") ~
             "Provision of MHPSS", 
             str_detect(activity_description, "MHPSS for children, adolescent and women") ~ 
               "Provision of MHPSS", 
             str_detect(activity, "Site Management, Coordination and Monitoring|Site Management Support") ~ 
               "Site Management, Coordination and Monitoring", 
             str_detect(activity, "Water tankering|Water stations in communities") ~ 
               "Provision of drinking water", 
             str_detect(activity, "Communal Toilet|Temporary Toilets") ~ 
               "Establishment of Temporary Toilets", 
             str_detect(activity, "Provision of essential and life-saving sexual and reproductive health medications|including dignity kits") ~ 
               "Lifesaving and essential supplies to women and girls (including dignity kits)", 
             str_detect(activity, "Installation/maintenance of WASH facility in school") ~ 
               "WASH in Schools", 
             str_detect(activity, "Distributing baby packs for the health and safety of infants|Baby kit") | 
               str_detect(activity, "Baby diapers") ~ 
               "Provision of Baby Kits", 
             str_detect(activity, "Distribution of critical WASH supplies (including hygiene kits) to affected households") | str_detect(activity_description, "Distribution of WASH hygiene kits") ~ "Distribution of critical WASH supplies (including hygiene kits) to affected households",
             str_detect(activity, "Nutrition education along food security interventions") ~ 
               "Nutrition Education",
             str_detect(activity, "NFI Distribution") ~ "Distriction of NFIs", 
             str_detect(activity, "Support to Temporary Learning Centers (Type -1) and Transitional learning centers (Type-2)") | str_detect(activity_description, "TLC set") ~ 
                          "Support to Temporary Learning Centers (Type -1) and Transitional learning centers (Type-2)",
             str_detect(activity, "Kitchen set") |
               str_detect(activity_description, "Supply of NFI - Kitchen Kit")
                 ~ "Provision of Kitchen Kits",
             str_detect(activity_description, "Disability inclusion and advocacy") ~ "Disability inclusion and advocacy", 
             TRUE ~ activity
           )) |> 
  left_join(
    cluster_activity_list, 
    by = c("activity" = "activity_cluster")
  ) 
```

```{r}
cluster_activity_list |> 
  filter(activity_cluster == "NFI Distribution (Mosquito net, baskets, bedsheets, mattress, Tarpaulins )")

activity_check |> 
  filter(is.na(in_cluster_list))
  glimpse()
```

```{r}
clean |> 
  filter(activity %in%)
```



Consolidation and standardisation of activities 
"Cash for work including community led debris removal" should be the same activity as "Cash for work including community led debris removal". 
Specific quantities should not be included in the activity column: 
"Distribution of 50 set of CP4E, 100 blanket and 50 food packages" should be 3 separate activities under 3 different sectors, with the quantities relegated to the appropriate columns. The same is true for "Distribution of Sanitation and Relief Supplies for Rasuwa Flood Response". 
Sector names should not be included in activities as this information is already collected in the sector column.
"Gender Based Violence (GBV) : Distribution of essential life saving supplies to women and girls (including dignity kits)"
Perhaps an issue for the Clusters, but I do not believe these two should be separate activities: 
"Provide psychosocial support to service providers ensuring caring for carers" 
"Provide targeted MHPSS in schools for students (children/adolescent)"
Activities with mixed modalities should also be separated into individual rows: 
"Support children to ensure their uninterrupted access to education and learning through cash and in-kind modalities" and the cash component reported as "Multipurpose Cash Support" under the Education sector. 
I would also argue that "Water tankering" and "Water stations in communities" should both be the same activity
The deployment of trained personnel such as in "Depolyment of Psychiatrist and Pyschologist" does not constitute an activity. Luckily, their activity description was clearer ("MHPSS for children, adolescent and women"). 
Activities such as "Support children to ensure their uninterrupted access to education and learning through cash and in-kind modalities" should re-classified as "Multipurpose Cash Support". 
Technical support for assessments does not count as 5W activity, I think. 


```{r}
activity_list <- read_csv("./data/Cluster_Activities - Sector_Activities.csv", skip = 2) |> 
  clean_names()
```


```{r}
cluster_activity_list |> 
  filter(str_detect(activity_cluster, "cash|Cash"))
```

```{r}
consolidated |> 
  mutate(activity_not_in_cluster_list = 
           ifelse(activity %out% cluster_activity_list$activity), 
         1, 0) |> 
   mutate_at(
    vars(households_reached, individuals_reached, 
         girls_18_yrs, boys_18_yrs, 
         women_18_yrs, men_18_yrs, 
         elderly_women_60_plus, 
         elderly_men_60_plus, 
         people_with_disabilities),
    ~replace_na(.x, 0)
  ) |> 
  mutate(sadd_total = girls_18_yrs + boys_18_yrs + women_18_yrs + men_18_yrs +
           elderly_women_60_plus + elderly_men_60_plus,
         sadd_check = individuals_reached - sadd_total) |>
  mutate(sadd_check_summary = case_when(
    sadd_check > 0 ~ "under", 
    sadd_check == 0 ~ "correct", 
    sadd_check < 0 ~ "over"
  ))
  
```





## Consolidated

```{r}
consolidated <- read_xlsx("./data/NEPAL 5W Data Consolidation (ADMIN_ONLY)_21 Sep 2026.xlsx", 
                          skip = 5, 
                          sheet = "Compiled_Data") |> 
  clean_names() |> 
  filter(disaster_response_plan %in% c("Rasuwa Flood Response", "Rasuwa Flood Respnese")) |> 
  mutate_at(c("province", "district", "municipality"), ~ str_to_title(.)) |> 
  mutate_at(c("province", "district", "municipality"), ~ str_trim(.)) |> 
  mutate(municipality = str_remove_all(municipality, " Gaunpalika"), 
         municipality = str_remove_all(municipality, " Municipality")) |>
  mutate(municipality = case_when(
    municipality == "Benighat" ~ "Benighat Rorang", 
    municipality == "Galchi Rural Municipality" ~ "Galchhi", 
    municipality == "Gandaki" ~ "Gandaki", 
    municipality == "Bheri Malika Municipality" ~ "Bheri Malika", 
    municipality == "Nalgad Municipality" ~ "Nalgad", 
    municipality == "Kathmandu Metropolitian City" ~ "Kathmandu", 
    municipality == "Nagarjun Municipality" ~ "Nagarjun", 
    municipality == "Belkotgadhi Municipality|Belkotgadhi Nagarpalika" ~ "Belkotgadhi", 
    str_detect(municipality, "Langtang") ~ "Langtang", 
    str_detect(municipality, "Bidur") ~ "Bidur", 
    municipality == "Kispang Municipality" ~ "Kispang", 
    municipality == "Tarkeshwor" ~ "Tarakeshwor", 
    municipality == "Rasuwa Dao, Dhunche" ~ "Gosaikunda",
    str_detect(municipality, "Devghat") ~ "Devghat", 
    str_detect(municipality, "Gandaki") ~ "Gandaki", 
    str_detect(municipality, "Belkotgadhi") ~ "Belkotgadhi", 
    str_detect(municipality, "Langtang") ~ "Langtang",
    municipality == "Aanbukhaireni" ~ "Aanbu Khaireni",
    TRUE ~ municipality)) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      filter(adm3_pcode != "NP0328596") |> 
      distinct(adm2_pcode, adm3_name, adm3_pcode), 
    by = c("adm2_pcode", "municipality" = "adm3_name")
  ) |> 
  rename(individuals_reached = total_number_of_beneficiaries_reached_people_individuals) |> 
  filter(disaster_response_plan == "Rasuwa Flood Response")
```



```{r}
consolidated <- read_xlsx("./data/NEPAL 5W Data Consolidation (ADMIN_ONLY) 20260917.xlsx", 
                          skip = 5, 
                          sheet = "Compiled_Data") |>
  janitor::clean_names() |> 
  mutate_at(c("province", "district", "municipality"), ~ str_to_title(.)) |> 
  mutate_at(c("province", "district", "municipality"), ~ str_trim(.)) |> 
  mutate(municipality = str_remove_all(municipality, " Gaunpalika")) |> 
  mutate(province = case_when(
    district == "Gorkha" ~ "Gandaki", 
    district == "Tanahu" ~ "Gandaki",
    TRUE ~ province
  )) |> 
  mutate(district = case_when(
    municipality == "Gosaikunda" ~ "Rasuwa", 
    municipality == "Bidur Municipality" ~ "Nuwakot", 
    TRUE ~ district
  )) |> 
  mutate(municipality = case_when(
    municipality == "Benighat" ~ "Benighat Rorang", 
    municipality == "Galchi Rural Municipality" ~ "Galchhi", 
    municipality == "Gandaki" ~ "Gandaki", 
    municipality == "Bheri Malika Municipality" ~ "Bheri Malika", 
    municipality == "Nalgad Municipality" ~ "Nalgad", 
    municipality == "Kathmandu Metropolitian City" ~ "Kathmandu", 
    municipality == "Nagarjun Municipality" ~ "Nagarjun", 
    municipality == "Belkotgadhi Municipality|Belkotgadhi Nagarpalika" ~ "Belkotgadhi", 
    str_detect(municipality, "Bidur") ~ "Bidur", 
    municipality == "Kispang Municipality" ~ "Kispang", 
    municipality == "Tarkeshwor" ~ "Tarakeshwor", 
    municipality == "Rasuwa Dao, Dhunche" ~ "Gosaikunda",
    str_detect(municipality, "Devghat") ~ "Devghat", 
    str_detect(municipality, "Gandaki") ~ "Gandaki", 
    str_detect(municipality, "Belkotgadhi") ~ "Belkotgadhi", 
    str_detect(municipality, "Langtang") ~ "Langtang",
    municipality == "Aanbukhaireni" ~ "Aanbu Khaireni",
    TRUE ~ municipality)) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_name, adm1_pcode), 
    by = c("province" = "adm1_name")
  ) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_pcode, adm2_name, adm2_pcode), 
    by = c("adm1_pcode", "district" = "adm2_name")
  ) |> 
  left_join(
    nepal_admin |> 
      distinct(adm1_pcode, adm2_pcode, 
             adm3_name, adm3_pcode), 
    by = c("adm1_pcode", "adm2_pcode", "municipality" = "adm3_name")
  ) |> 
  rename(individuals_reached = total_number_of_beneficiaries_reached_people_individuals) |> 
  filter(disaster_response_plan == "Rasuwa Flood Response")

```

## Errors

```{r}
consolidated |> 
  filter(relief_item_unit == "Meter") |> 
  sample_n(3) |> 
  pull(activity)
```


```{r}
consolidated |> glimpse()
consolidated |> count(activity_status)
```


```{r}
cluster_activity_list <- read_csv("./data/Cluster_Activities - Sector_Activities.csv", skip = 2) |> 
  clean_names() |> 
      mutate(in_cluster_list = 1) |> 
      filter(!is.na(activity))
```

```{r}
consolidated_error_checking <- consolidated |> 
  replace_na(
    list(households_reached = 0, 
         individuals_reached = 0, 
         girls_18_yrs = 0, 
         boys_18_yrs = 0, 
         women_18_yrs = 0, 
         men_18_yrs = 0,
         elderly_women_60_plus = 0, 
         elderly_men_60_plus = 0, 
         people_with_disabilities = 0)
  ) |> 
  mutate(
    sadd_total = girls_18_yrs + boys_18_yrs + women_18_yrs + men_18_yrs +
           elderly_women_60_plus + elderly_men_60_plus,
    sadd_check = individuals_reached - sadd_total
  ) |> 
  mutate(
    sadd_check_summary = case_when(
    sadd_check > 0 ~ "under", 
    sadd_check == 0 ~ "correct", 
    sadd_check < 0 ~ "over"
  )) |> 
  mutate(
    
    admin_error = case_when(
    district == "Nuwakot, Rasuwa" ~ "district error", 
    is.na(municipality) ~ "municipality missing", 
    municipality %in% c("Tarkeshwar") ~ "municipality error",
    TRUE ~ NA_character_),
    
    ward_error = case_when(
      is.na(ward) ~ "ward missing", 
      ward > 20 ~ "ward error", 
      TRUE ~ NA_character_
    ), 
    
    sector_error = case_when(
      sector %in% c("Multi-Purpose Cash") ~ "sector spelling", 
      is.na(sector) ~ "missing sector", 
      TRUE ~ NA_character_
    ), 
    
    activity_error = case_when(
      is.na(activity) ~ "activity missing", 
      activity %out% (cluster_activity_list$activity) ~ "activity not in cluster list", 
      TRUE ~ NA_character_
    ), 
    
    location_type_error = case_when(
      is.na(location_type) ~ "location type missing", 
      location_type == "Holding Center/Community" ~ "merged location type", 
      TRUE ~ NA_character_
    ), 
    
    relief_item_unit_error = case_when(
      relief_item_unit %in% c("Items", "Number", "Packet") ~ "unit unclear", 
      relief_item_unit %in% c("PAC", "Box", "Piece", "Meals", 
                              "Sachet", "Pairs", "Drum", "Strip", 
                              "N/A", "Pcs", "set", "Cylinder", "Meter") ~ "unit error", 
      relief_item_unit %in% c("kg", "Tons") ~ "unit typo", 
      TRUE ~ NA_character_
    ), 
    
    activity_status_error = ifelse(is.na(activity_status), "activity status missing", NA_character_)
    
    ) 
  
  

```



```{r}
consolidated |> filter(disaster_response_plan == "Rasuwa Flood Response") |> count(district)
```

```{r}
consolidated |> filter(disaster_response_plan == "Rasuwa Flood Response") |> count(municipality)

affected_wards |> distinct(adm2_en, adm3_en)
```

Jwalamukhi, Kathmandu, Likhu, Nagarjun, Naukunda, Nilkhantha Municipality, Shivapuri, Suryagadhi are not affected by the flooding. Are these holding centres? If not, partners need to clarify the relevance of these activities to the response 

```{r}
consolidated |> filter(disaster_response_plan == "Rasuwa Flood Response") |> 
  count(sector)
```

```{r}
consolidated |> 
  filter(disaster_response_plan == "Rasuwa Flood Response") |> 
  filter(is.na(activity))
```



```{r}
consolidated |> 
  count(activity) |> 
  mutate(response_modality = case_when(
    str_detect(actvity, "Cash for work|Cash transfer|Multi-purpose cash transfer|through cash and in-kind modalities") ~ 
      # Cash
      "Cash/Voucher", 
    str_detect(activity, "Distributing baby packs|Distribution of recreational kits|Distribution of winterization Kits to children|Distribution of Early Childhood Development (ECD) kits|Distribution of Water purifier|Distribution of critical WASH supplies|Distribution of elderly kits|Distribution of in-kind Food Relief|Distribution of learning packs|Distribution of textbooks|Distribution of water purifier|First Aid Kit|Distribution of essential life saving supplies to women and girls (including dignity kits)|Generator Support - 2.5KW|HH chlorination supplies (like Piyush, Aquatabs etc.)|Kitchen set distribution|NFI Distribution|Provide micronutrient supplements|Provide the assistive devices|Provision of essential and life-saving sexual and reproductive health medications|Provision of essential medicines, supplies and device|Provision of hygiene and sanitation materials|Provision of ready to eat|Solar Light|Support to Temporary Learning Centers (Type -1)|Support municipalities for office supplies|Water storage supplies like HH buckets, tanks") ~ 
      # In-kind
      "In-kind assistance", 
    str_detect(activity, "Establishment of child friendly spaces|Support to child protection transit home|Support to unaccompanied, separated and other vulnerable children affected by|SRH outreach program including mobile clinics to provide life-saving interventions|Deployment of Female Community Health Volunteers|Deployment of Mobile Medical Team|Depolyment of Psychiatrist and Pyschologist|Establishment of women friendly spaces|Provision of GBV response services|Integrate psychosocial support services|Major maintenance|Provision of psychosocial support|Provide psychosocial support|Provide targeted MHPSS|Screening of 6-59 months|Tecnical Support|Treatment of Severe Acute Malnutrition|Veterinary treatment and management|Water quality test|Water stations in communities|Water supply in Schools|Water tankering|") ~
      # Service delivery
      "Service delivery/support", 
    str_detect(activity, "Orientation/training|Sensitization/orientation|Capacity building|teacher training on psychosocial support") ~ 
      # Capacity building
      "Capacity building/Training", 
    str_detect(activity, "Communal Toilet|Emergency Shelter and repair Support|Emergency transitional shelter|Establish Temporary/Makeshift hospital or health facility|Installation/maintenance of WASH facility in school|Temporary Toilets") ~ 
      # Reconstruction
      "Repair/Reconstruction/Construction",
    str_detect(activity, "Information sharing and awareness sessions|General Hygiene promotion|Community sensitization|PSA messaging|Promotion and awareness") ~
      # Advocacy
      "Awareness/Advocacy", 
    str_detect(activity, "Logistics Coordination and Information Management|Procurement and Supply Chain coordination|Site Management Support benefiting affected individuals through coordination|Site level service mapping and gap identification|Site management support|Site-level service monitoring and gap identification|Support to Common Warehousing|Common Transport from Kathmandu HSA") | activity == "Other" ~ 
      # Other
      "Other", 
    TRUE ~ NA_character_
    
  ))
```




A total of 73,784 individuals have been reached in Gosaikunda Municipality across the  Food Security, Protection, Shelter and WASH Clusters. 

A total of 546 individuals have been reached in Kalika Municipality across the Food Security and Health Clusters. 

A total of 1,260 individuals have been reached in Uttargaya Municipality across the Food Security, Health and Protection and Shelter Clusters. 


 Food Security, Protection, Shelter and WASH



### Planned/Reached Municipality

```{r planned-reach-municipality, fig.height=8}
consolidated |> 
  mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
         sector = ifelse(str_detect(sector, "Health"), "Health", sector)) |> 
  filter(sector %out% c("ETC", "Logistics") & !is.na(sector)) |> 
  filter(province != "Karnali") |>
  # Remember to allow Kathmandu back in when they have more people who have been reached
  filter(district != "Kathmandu") |> 
  group_by(province, district, municipality, sector, adm3_pcode) |> 
  summarise(
    individuals_targeted = sum(people_targeted_individuals, na.rm = TRUE), 
    individuals_reached = sum(individuals_reached, na.rm = TRUE), 
    .groups = "drop"
  ) |>  
  mutate(label = paste0(municipality, ", ", district)) |> 
  filter(individuals_targeted != 0 | 
           individuals_reached != 0) |> 
  mutate(individuals_targeted = 
           ifelse(individuals_targeted == 0 & individuals_reached != 0, 
                  individuals_reached, individuals_targeted)) |> 
  left_join(
    affected_wards_population |>
      group_by(adm3_pcode) |>
      summarise(
        estimated_affected_population = sum(estimated_affected_population, na.rm = TRUE)),
    by = "adm3_pcode") |> 
  pivot_longer(cols = c(individuals_targeted, 
                        individuals_reached, 
                        estimated_affected_population), 
               names_to = "variable", 
               values_to = "value") |> 
  mutate(variable = str_replace_all(variable, "_", " "), 
         variable = str_replace_all(variable, "individuals", "beneficiaries"), 
         variable = str_to_title(variable), 
         variable = fct_relevel(variable,
                                c("Beneficiaries Targeted", 
                                  "Beneficiaries Reached", 
                                  "Estimated Affected Population"))) |> 
  ggplot(aes(x = value, y = municipality)) + 
  geom_col(aes(fill = fct_rev(variable)), position = position_dodge()) + 
  scale_fill_brewer(palette = "BuPu", direction = -1) +
  # scale_fill_viridis_d() + 
  scale_x_continuous(labels = comma) + 
  facet_wrap(~district, scales = "free", 
             ncol = 2) +
  guides(fill = guide_legend(reverse = TRUE)) +
  labs(x = "",  
       y = "Municipality", 
       title = "Planned, Reached and Estimated Affected Population by Municipality",
       subtitle = "as of 20260907, figures listed are beneficiaries frequencies, not individuals; from the 5Ws", 
       fill = "") +
   theme(strip.background = element_rect(fill = "black"), 
         strip.text = element_text(size = 13), 
         axis.text.y = element_text(size = 13))
   
ggsave("./plots/planned_reached_municipality.png", height = 8, width = 12)
```



```{r}
consolidated |> 
  mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
         sector = ifelse(str_detect(sector, "Health"), "Health", sector)) |> 
  filter(sector %out% c("ETC", "Logistics") & !is.na(sector)) |> 
  filter(province != "Karnali") |> 
  group_by(province, district, municipality, sector, adm3_pcode) |> 
  summarise(
    individuals_targeted = sum(people_targeted_individuals, na.rm = TRUE), 
    individuals_reached = sum(individuals_reached, na.rm = TRUE), 
    .groups = "drop"
  ) |>  
  mutate(label = paste0(district, ", ", municipality)) |> 
  filter(individuals_targeted != 0 | 
           individuals_reached != 0) |> 
  mutate(individuals_targeted = 
           ifelse(individuals_targeted == 0 & individuals_reached != 0, 
                  individuals_reached, individuals_targeted)) |> 
  left_join(
    affected_wards_population |>
      group_by(adm3_pcode) |>
      summarise(
        estimated_affected_population = sum(estimated_affected_population, na.rm = TRUE)),
    by = "adm3_pcode") |> 
  pivot_longer(cols = c(individuals_targeted, 
                        individuals_reached), 
               names_to = "variable", 
               values_to = "value") |> 
  mutate(variable = str_replace_all(variable, "_", " "), 
         variable = str_to_title(variable)) |> 
  ggplot(aes(x = value, y = label)) + 
  geom_col(aes(fill = variable), position = position_dodge()) + 
  scale_fill_viridis_d(begin = .5) + 
  scale_x_continuous(labels = comma) + 
  facet_wrap(~sector, scales = "free", 
             ncol = 1) +
  labs(x = "", 
       y = "Municipality and District", 
       title = "Planned, Reached and Estimated Affected Population by Municipality", 
       fill = "") +
   theme(strip.background = element_rect(fill = "black"), 
         title = element_text(size = 9))

ggsave("./plots/planned_reached_sectors.png", height = 11, width = 8)
  
```


```{r}
consolidated |> 
  filter(municipality == "Gosaikunda" & sector == "WASH") |> 
  group_by(sector) |> 
  summarise(individuals_reached = sum(individuals_reached, na.rm = TRUE), 
            individuals_targeted = sum(people_targeted_individuals, na.rm = TRUE))
```

### Sector agencies map

```{r}
consolidated |> 
  filter(!is.na(district) & is.na(adm2_pcode))
```

```{r}
nepal_admin |> 
  filter(adm2_name == "Nuwakot")
```


```{r}
consolidated |> 
  mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
         sector = ifelse(str_detect(sector, "Health"), "Health", sector)) |> 
  filter(sector %out% c("ETC")) |> 
  filter(province != "Karnali") |> 
  mutate(adm2_pcode = ifelse(str_detect(district, "Nuwakot") & is.na(adm2_pcode), "NP0328", adm2_pcode)) |> 
  mutate(duplicate = ifelse(
    implementing_partner == lead_agency, 
    1, 0
  )) |> 
  mutate(implementing_partner = ifelse(
    duplicate == 1, NA_character_, implementing_partner
  )) |> 
  pivot_longer(
    lead_agency:implementing_partner, 
    names_to = "role",
    values_to = "agencies"
  ) |> 
  filter(!is.na(agencies)) |>  
  filter(!is.na(sector)) |> 
  mutate(is_un = ifelse(
    str_detect(agencies, "UNICEF|IOM|WFP|UNFPA|FAO|UN Women|WHO|UNDP|UNOPS"), 
    1, 0
  )) |> 
  filter(is_un == 1) |>
  select(-is_un) |> 
  distinct(adm2_pcode, district, adm3_pcode, municipality, agencies) |> 
  filter(!is.na(municipality) | !is.na(adm3_pcode)) |> 
  group_by(
    adm2_pcode, district, adm3_pcode, 
    municipality
  ) |> 
  summarise(num_un_agencies = n_distinct(agencies),
            un_agencies = paste0(agencies, collapse = ", ")) |> 
  
  filter(municipality %out% c("Kathmandu", "Shivapuri", "Langtang",
                              "Kakani", "Myagang")) |> 
  write_csv("./data/un_agencies_by_municipality_20260921.csv")


    left_join(
    adm3 |> 
      filter(adm2_name %in% c("Nuwakot", "Dhading", "Gorkha", "Tanahu", "Rasuwa", "Chitawan")), 
    by = c("adm2_pcode", "adm3_pcode")) |> 
  st_as_sf() |> 
  ggplot() + 
  geom_sf(size = .1, aes(fill = fill)) + 
  geom_sf_text(aes(label = adm3_name), size = 2.2, alpha = .7, colour = "red", nudge_y = -0.01) +
  geom_sf_text(aes(label = un_agencies), size = 2.4) +
  scale_fill_manual(values = c("a" = "lightblue"), na.value = "white") +
  theme(legend.position = "none", 
        strip.background = element_rect(fill = "black")) + 
  labs(title = "Presence of UN agencies in Municiaplities in Chitawan, Dhading, Gorkha, Nuwakot, Rasuwa and Tanahu districts", 
       x = "", y = "") 
  
ggsave("./plots/un_agencies_municipality.png", height = 9, width = 15, units = "in")

  write_csv("./data/un_agencies_by_municipality.csv")

  group_by(district, municipality) |> 
  summarise(un_agencies = n_distinct(agencies)) |> 
  write_csv("./data/un_agencies_count_by_municiplity.csv")
  
adm3 |> glimpse()
```

Chitawan NP0335 Ichchha Kamana NP0335401





Ichchha Kamana
Benighat Rorang
Gajuri
Galchhi
Siddhalek
Gandaki
Shahid Lakhan
Belkotgadhi
Bidur
Kispang
Tarakeshwor
Gosaikunda
Kalika
Aama chhodingmo
Uttargaya
Aanbu Khaireni
Devghat

```{r}
affected_municipalities_wards |>
  left_join(nepal_admin |> distinct(adm3_name, adm3_pcode), 
            by = "adm3_pcode") |> 
  count(adm3_name)

Belkotgadhi
Kispang
```

```{r}
consolidated |> 
   mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
         sector = ifelse(str_detect(sector, "Health"), "Health", sector)) |>
  filter(sector %out% c("ETC")) |> 
  filter(province != "Karnali") |> 
```


```{r}
consolidated |> 
  mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
         sector = ifelse(str_detect(sector, "Health"), "Health", sector)) |> 
  filter(sector %out% c("ETC", "Logistics") & !is.na(sector)) |> 
  filter(province != "Karnali") |>
  group_by(district, adm2_pcode, municipality, adm3_pcode, sector, lead_agency, implementing_partner) |> 
  summarise(
    frequencies = sum(individuals_reached, na.rm = TRUE), 
    .groups = "drop"
  ) |> 
  mutate(duplicate = ifelse(
    implementing_partner == lead_agency, 
    1, 0
  )) |> 
  mutate(implementing_partner = ifelse(
    duplicate == 1, NA_character_, implementing_partner
  )) |> 
  pivot_longer(
    lead_agency:implementing_partner, 
    names_to = "role",
    values_to = "agencies"
  ) |> 
  select(-frequencies, -duplicate) |> 
  filter(!is.na(agencies)) |>  
  group_by(district, adm2_pcode, municipality, adm3_pcode, sector) |> 
  summarise(num_agencies = n_distinct(agencies), 
            agencies_text = paste(agencies, collapse = ",")) |> 
  right_join(
      adm3 |> filter(adm2_name %in% c("Dhading", "Nuwakot", "Gorkha", 
                                "Jajarkot", "Kathmandu", "Mugu", 
                                "Rasuwa", "Tanahu")), 
      by = c("adm2_pcode", "adm3_pcode")
  ) |> 
  filter(!is.na(municipality) & !is.na(sector)) |> 
  mutate(num_agencies = as.numeric(num_agencies)) |> 
  st_as_sf() |> 
  ggplot() +
  geom_sf(aes(fill = num_agencies), linewidth =.1) +
  geom_sf_text(aes(label = municipality), size = 2) +
  scale_fill_continuous(palette = "Blues", 
                        breaks = seq(1, 20, 2), 
                        guide = guide_colorbar(barheight = unit(6, "cm"))) +
  # scale_fill_viridis(direction = -1) + 
  facet_wrap(~sector) + 
  labs(title = "Number of agencies by sector, by municipality", 
       subtitle = "as of 202609076, from the 5Ws",
       x = "", y = "", 
       fill = "Number of\nagencies") + 
  theme(strip.background = element_rect(fill = "black"), 
        axis.text.x = element_text(size = 5), 
        axis.text.y = element_text(size = 5), 
        panel.grid.major = element_line(color = "gray90"),
        panel.grid.minor = element_line(color = "gray90"))
  
ggsave("./plots/sector_agencies_map_blues.png", height = 7, width = 11, units = "in")
```


```{r}
consolidated |> 
  filter(province != "Karnali") |> 
  group_by(response_modality) |> 
  summarise(individuals_reached = sum(individuals_reached, na.rm = TRUE)) |> 
  arrange(desc(individuals_reached)) |> 
  filter(individuals_reached != 0) |> 
  mutate(response_modality = ifelse(is.na(response_modality), 
                                    "N.A.", response_modality)) |> 
  mutate(pc = round(individuals_reached / sum(individuals_reached) * 100, 2)) |> 
  rename(`Response modality` = response_modality, 
         `Beneficiary frequencies` = individuals_reached, 
         `%` = pc) |> 
  flextable() |> 
  theme_zebra() |> 
  save_as_image("./plots/response_modality.png")

consolidated |> 
  filter(is.na(response_modality)) |> 
  count(activity_description, sort = TRUE)

consolidated |> filter(is.na(activity))
```


```{r}
consolidated |> 
  group_by(activity) |> 
  summarise(
    individuals_reached = sum(individuals_reached, na.rm = TRUE), 
    individuals_targeted = sum(people_targeted_individuals, na.rm = TRUE)
  ) |> 
  arrange(desc(individuals_reached)) |>
  rename(
    Activity = activity, 
    `Individuals reached` = individuals_reached, 
    `Individuals targeted` = individuals_targeted
  ) |> 
  head(10) |> 
  # mutate(activity = str_sub(activity, start = 1L, end = 70L)) |> 
  flextable() |> 
  flextable::set_caption(as_paragraph(as_chunk("Top 10 activities by individuals reached"))) |> 
  theme_zebra() |> 
  flextable::width(width = 3) |> 
  save_as_image("./plots/top_activities.png")
```


```{r}
adm3 |> filter(adm2_name %in% c("Dhading", "Nuwakot", "Gorkha", 
                                "Jajarkot", "Kathmandu", "Mugu", 
                                "Rasuwa", "Tanahu"))

adm3 |> 
  filter(adm1_name %in% c("Bagmati", "Gandaki")) |> 
  st_as_sf() |> 
  ggplot() +
  geom_sf(size = .1) + 
  geom_sf_text(aes(label = adm2_name), size = 1) +
  geom_sf_text(aes(label = adm3_name), size = 1.5)
  
nepal_admin |> filter(str_detect(adm3_name, "Langtang"))
```

### Ward-level tables

```{r}
read_csv("./data/differences_between_flash_appeal_and_rdna_affected_wards.csv") |> 
  select(-different) |> 
  left_join(impacted_buildings |> 
      select(adm3_pcode, ward, impacted_buildings), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(
    read_csv("./data/nepal_census2021_ward_level_household_tables_bagmati_gandaki_flat.csv") |> 
      select(adm3_pcode, ward, 
             total_households 
             ), 
    by = c("adm3_pcode", "ward")
  ) |>
  left_join(
    consolidated |> 
    filter(!is.na(sector)) |> 
    mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
           sector = ifelse(str_detect(sector, "Health|Nutrition"), "Health & Nutrition", sector)) |> 
    filter(ward < 20 & individuals_reached > 0) |> 
    group_by(adm3_pcode, ward, sector) |> 
    summarise(individuals_reached = sum(individuals_reached)) |> 
    pivot_wider(names_from = sector, 
                values_from = individuals_reached, 
                names_glue = "{sector}_{.value}"), 
    by = c("adm3_pcode", "ward")
  ) |>
  rename_with(~ str_replace_all(.x, "_", " ")) |>
  writexl::write_xlsx("./data/nepal_floods_ward_level_data.xlsx")


  write_csv("./data/nepal_floods_ward_level_data.csv")

differences |> 
  select(-match3, -different) |> 
  left_join(
    impacted_buildings |> 
      select(adm3_pcode, ward, impacted_buildings), 
    by = c("adm3_pcode", "ward")
  ) |> 
  left_join(
    census_working |> 
      select(adm3_pcode, ward, 
             total_households), 
    by = c("adm3_pcode", "ward")
  ) |>
  left_join(
    consolidated |>
    filter(!is.na(sector)) |> 
    mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
           sector = ifelse(str_detect(sector, "Health|Nutrition"), "Health & Nutrition", sector)) |> 
    filter(ward < 20 & individuals_reached > 0) |> 
    group_by(adm3_pcode, ward, sector) |> 
    summarise(individuals_reached = sum(individuals_reached)) |> 
    pivot_wider(names_from = sector, 
                values_from = individuals_reached, 
                names_glue = "{sector}_{.value}"), 
    by = c("adm3_pcode", "ward")
  ) |>
  rename_with(~ str_replace_all(.x, "_", " ")) |>
  writexl::write_xlsx("./data/nepal_floods_ward_level_data.xlsx")

municipal_damage_losses
    
```
  
```{r}
municipal_damage_losses <- read_csv("./data/municipal_damage_loss.csv")
```

```{r}
municipal_damage_losses |> 
  select(district, adm2_pcode, municipality, adm3_pcode, 
         affected_wards, number_of_affected_wards, 
         population_in_affected_wards_census_2021, 
         households_in_affected_wards_census_2021, 
         impacted_buildings) |>
  filter(!is.na(affected_wards)) |> 
  left_join(
    consolidated |> 
      mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
           sector = ifelse(str_detect(sector, "Health|Nutrition"), "Health & Nutrition", sector)) |> 
      filter(disaster_response_plan == "Rasuwa Flood Response") |> 
      group_by(sector, adm3_pcode, municipality) |> 
      summarise(
        individuals_reached = sum(individuals_reached, na.rm = TRUE)
      ) |> 
      filter(!is.na(municipality) & !is.na(adm3_pcode) & !is.na(sector)) |> 
      pivot_wider(
        names_from = sector, 
        values_from = individuals_reached, 
        names_glue = "{sector}_{.value}") |> 
      select(-municipality), 
  by = c("adm3_pcode")
  ) |> 
  rename_with(~ str_replace_all(.x, "_", " ")) |> 
  writexl::write_xlsx("./data/municipal_summary_for_umesh.xlsx")
  write_csv("./data/municipal_summary_for_umesh.csv")


```

## Extracts -- Sector


```{r}
consolidated |> 
  filter(sector == "Food Security") |>
  group_by(
    province, district, municipality, ward,
    adm1_pcode, adm2_pcode, adm3_pcode
  ) |> 
  replace_na(
    list(people_targeted_individuals = 0, 
         individuals_reached = 0)
  ) |> 
  summarise(
    individuals_targeted_max = max(people_targeted_individuals, na.rm = TRUE), 
    individuals_targeted_sum = sum(people_targeted_individuals, na.rm = TRUE),
    individuals_reached_max = max(individuals_reached, na.rm = TRUE), 
    individuals_reached_sum = sum(individuals_reached, na.rm = TRUE)
  ) |> 
  full_join(
    consolidated |> 
  mutate(sector = ifelse(str_detect(sector, "Protection"), "Protection", sector), 
         sector = ifelse(str_detect(sector, "Health"), "Health", sector)) |> 
  filter(sector %out% c("ETC")) |> 
  filter(province != "Karnali") |> 
  mutate(adm2_pcode = ifelse(str_detect(district, "Nuwakot") & is.na(adm2_pcode), "NP0328", adm2_pcode)) |> 
  mutate(duplicate = ifelse(
    implementing_partner == lead_agency, 
    1, 0
  )) |> 
  mutate(implementing_partner = ifelse(
    duplicate == 1, NA_character_, implementing_partner
  )) |> 
  pivot_longer(
    lead_agency:implementing_partner, 
    names_to = "role",
    values_to = "agencies"
  ) |> 
  filter(!is.na(agencies)) |>  
  filter(!is.na(sector)) |>
  filter(!is.na(municipality) | !is.na(adm3_pcode)) |> 
  filter(sector == "Food Security") |> 
  distinct(adm2_pcode, adm3_pcode, ward, agencies) |>  
  
  group_by(
    adm2_pcode, adm3_pcode, ward) |> 
  summarise(num_agencies = n_distinct(agencies), 
            agencies = paste0(agencies, collapse = ", ")), 
  by = c("adm2_pcode", "adm3_pcode", "ward")
  ) |> 
  write_csv("./data/food_security_5ws_extract_20260917.csv")
```


  
## Contacts

  
```{r}
contact_list <- read_csv("./data/Nepal Flood Response Contact List - Contact List.csv", 
         skip = 2) |> 
  janitor::clean_names() |> 
  mutate(agency = case_when(
    str_detect(agency, "CWIN|cwin|Cwin|CWIN-|CWIM- NEPAL") ~ "CWIN-Nepal", 
    str_detect(agency, "DFAT|Australian Department of Foreign Affairs and Trade") ~ "DFAT", 
    str_detect(agency, "Habitat for Humanity") ~ "Habitat for Humanity", 
    str_detect(agency, "FAIR MED / MANK") ~ "MANK and FAIR MED", 
    str_detect(agency, "Nepal Red Cross Society|Nepal Redcross Society") ~ "Nepal Red Cross Society", 
    str_detect(agency, "OM ") ~ "Operation Mobilisation", 
    str_detect(agency, "Plan International") ~ "Plan International", 
    str_detect(agency, "Save the Children") ~ "Save the Children", 
    str_detect(agency, "UN Women") ~ "UN Women", 
    str_detect(agency, "UNESCO") ~ "UNESCO", 
    str_detect(agency, "UNFPA") ~ "UNFPA", 
    str_detect(agency, "UNODC") ~ "UNODC", 
    str_detect(agency, "Unicef") ~ "UNICEF", 
    str_detect(agency, "WFP|World Food Programme") ~ "WFP", 
    str_detect(agency, "World Health Organization") ~ "WHO", 
    str_detect(agency, "One heart worldwide") ~ "One Heart Worldwide", 
    TRUE ~ agency
  )) 

contact_list |> count(agency)

contact_list |> write_csv("./data/contact_list_agencies_cleaned_20260907.csv")
```


### FTS


```{r}

tribble(
  ~type, ~value, ~source, ~label,
  "Funded", 21.0, "fts", "Funded $21 M", 
  "Unmet", 28.6, "fts", "Unmet $28.6 M"
) |> 
  ggplot(aes(x = value, y = source)) + 
  geom_col(aes(fill = fct_rev(type)), width = .1) + 
  scale_fill_manual(values = c("Funded" = "#009edb", "Unmet" = "#e3edf6")) + 
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.5))
  
```



